### 2016-05-13 2016_ICML/rebuttal.txt
ICML submission

We thank all reviewers for their constructive reviews. We can only provide feedback to the most significant points:

R1: The main empirical results claimed by the authors show that MRS can do better than methods such as ES when compared using the mean regret. This could also be a result of the more global exploration performed by ES
A: Actually, we observed empirically that ES explores more locally relative to MRS (compare Figure 3). We will try to relate the results obtained in the paper to the references provided by the reviewer.

R2: The abstract and introduction sound like Bayesian Optimization is always about minimizing regret. This is not true.
A: With "regret", we were referring to the immediate regret as defined in Section 3 which is defined based on the final recommendation of the algorithm for the optimum after N evaluations. We will clarify that BO is not about minimizing the regret notion used in the bandit literature (defined on the obtained function values during optimization).

R2: It is unclear at this point whether PES is actually cheaper than ES, as the authors claim. [...]
A: We will remove any assessment stating PES being superior compared to ES and refer the reader to external literature for a cpmparison of the two approaches.

R3: The problem formulation of optimizing the expected regret reduction (ERR) at the best point \tilde{x_n} appears to have a fundamental problem: it fixes \tilde{x_n} and then tries to change the predictive distribution to maximally reduce the regret of this fixed \tilde{x_n} under the predictive distribution. (MRS has exactly the same problem, only that it does this for multiple fixed \tilde{x_n} in a Bayesian fashion.)
A: The \tilde{x} in the first and second term of a_MRS are not fixed but drawn from different distributions ("p^\star_n" versus "p^\star_{\mathcal{D}_n \cup \{(x^q, y)\}"). Thus, MRS does not fix \tilde{x_n} (not even in a Bayesian fashion since the distributions are different).

Related to this: we noticed after submission that there was a mistake in our definition of MRS^{point} (the implementation was correct). It should have been:

a_{MRS^point}(x^q)
     = \min_{\tilde x} ER(p_n)(\tilde x)
       - E_{y \vert p_n(f), x^q}[\min_{\tilde x}  ER(p^{[x^q, y]}_n)(\tilde x)]

Note that different minimizers \tilde{x} in the first and second term may be chosen. Thus, \tilde{x} is also not fixed for MRS^{point}. We apologize for the confusion caused by this mistake.

R3: "Thus, sampling in this parameter range can reduce the expected regret considerably either by confirming that the true value of f(x) on x >= 3.5 is actually as small as expected or by switching \tilde{x}_{n+1} to this area if f(x) turns out to be large." I fully agree with this statement, but the problem with MRS is that it only targets the first of these terms (confirming that the current \tilde{x_n} is good) and not the second (gathering information that makes us change \tilde{x}_{n+1}).
A: Whether the first or second case occur depends on the observed function value and is not a choice of the algorithm. Figure 1 actually shows an example where MRS samples at points which reveal little about the function value at \tilde{x_n}=1.5 but which have a small chance of changing \tilde{x}_{n+1} to 4.0.

R3: What is the performance of UCB and MRS in Experiment 1 with N=200, in terms of mean and median?
A: We ran 50 repetitions of GP-UCB and MRS for N=200. We must not include any URLs or graphics in this rebuttal so we can summarize the results only verbally: Both GP-UCB and MRS reach the same level of immediate regret after 200 steps (in mean and median) with no significant difference according to a Wilcoxon signed-rank test.

R3: While some experiments without model mismatch are useful, there should also be some with it.
A:  We performed a similar experiment as in Section 3.2 of Henning and Schuler, where the functions are sampled from a GP prior with rational quadratic kernel but the model used in the optimizer was based on an RBF kernel (thus there is model-mismatch). The empirical findings are qualitatively very similar to those in Figure 2; the main difference being that all methods incur higher immediate regret relative to the setting without model-mismatch (nearly one order of magnitude).

Additional remarks:
 * The principal concerns about changing the acquisition function and the "recommender" for the final choice at the same time are valid. However, we used the same recommender for all acquisition functions, namely the maximizer of GP model. Note that this maximizer is also the point of minimum expected immediate regret for a GP (not to be confused with maximizer of the expected regret reduction). We will clarify this point in the revised version of the paper.

 * The choice of kappa=5 for UCB in Sec. 5.2 was not arbitrary but based on preliminary experiments comparing five different values for kappa and GP-UCB (fixed kappa=5 being the best).

### 2016-05-13 2016_ICML/cmrs.tex
ICML submission

\documentclass{article} % For LaTeX2e

\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

\usepackage{graphicx}

\usepackage{amsmath,amssymb}
\def\D{\mathrm{d}}

\usepackage{umoline}
%\newcommand{\todo}[2]{\Underline{#1}\textbf{ [\scriptsize TODO: #2] }}
\newcommand{\todo}[2]{#1}

\graphicspath{{.}{pics/}}

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
%\usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
\usepackage[accepted]{icml2016}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Minimum Regret Search for Single- and Multi-Task Optimization}

\begin{document}

\twocolumn[
\icmltitle{Minimum Regret Search for Single- and Multi-Task Optimization}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2015
% package.
\icmlauthor{Jan Hendrik Metzen}{janmetzen@mailbox.org}
\icmladdress{Universit{\"a}t Bremen, 28359 Bremen, Germany \&
             Robert Bosch GmbH, 70442 Stuttgart, Germany}
%\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
%\icmladdress{Their Fantastic Institute,
%            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Bayesian Optimization, Contextual Policy Search, Multi-Task Learning, Gaussian Process}

\vskip 0.3in
]

%\maketitle

\begin{abstract}
We propose minimum regret search (MRS), a novel acquisition function for Bayesian
optimization. MRS bears similarities with information-theoretic approaches
such as entropy search (ES). However, while ES aims in each query at maximizing the
information gain with respect to the global maximum, MRS aims at minimizing the
expected immediate regret of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
cases, MRS produces fewer outliers with high regret than ES. We provide empirical
results both for a synthetic single-task optimization problem as well as for a
simulated multi-task robotic control problem.
\end{abstract}

\section{INTRODUCTION}

Bayesian optimization \citep[BO,][]{shahriari_taking_2016} denotes a sequential,
model-based, global approach for optimizing black-box functions that are
non-convex, do not necessarily provide derivatives, are expensive to evaluate (either
computationally, economically, or morally), and are potentially noisy. Under
these conditions, there is typically no guarantee for finding the true optimum of the
function with a finite number of function evaluations. Instead, one often aims
at finding a solution which has small regret with regard to the true optimum. BO
aims at finding such a solution of minimum regret while  minimizing at the same
time the number of evaluations of the expensive target function. For this, BO
maintains a probabilistic surrogate model of the objective function, and a
myopic utility or acquisition function, which defines the ``usefulness'' of
performing an additional function evaluation at a certain input for learning about the optimum.

BO has been applied to a diverse set of problems, ranging from automatic  machine
learning \cite{bergstra_algorithms_2011,snoek_practical_2012} over robotics
\cite{calandra_bayesian_2015,lizotte_automatic_2007,kroemer_combining_2010,alonso_an_2015} to
sensor networks \cite{srinivas_gaussian_2010} and environmental monitoring
\cite{6385653}. For a more comprehensive overview of application areas, we refer
to \citet{shahriari_taking_2016}.

A critical component for the performance of BO is the acquisition function,
which controls the exploratory behavior of the sequential search procedure.
Different kinds of acquisition functions have been proposed, ranging from
improvement-based acquisition functions over optimistic acquisition functions to
information- theoretic acquisition functions (see Section
\ref{Section:Background}). In the latter class, the group of entropy
search-based approaches
\cite{villemonteix_informational_2008, hennig_entropy_2012,hernandez-lobato_predictive_2014}, which aims at maximizing the information gain regarding
the true optimum, has achieved state-of-the-art performance on a number of
synthetic and real-world problems. However, performance is often reported as the
median over many runs, which bears the risk that the median masks ``outlier'' runs that
perform considerably worse than the rest. In fact, our results indicate that
the performance of sampling-based entropy search is not necessarily better
than traditional and cheaper acquisition functions according to the mean immediate regret.

In this work, we propose minimum regret search (MRS), a novel acquisition
function that explicitly aims at minimizing the expected immediate regret
(Section \ref{Section:MRS}). MRS performs well according to both the mean and
median performance on a synthetic problem (Section
\ref{Section:ResultsSingleTask}). Moreover, we discuss how MRS can be extended
to multi-task optimization problems (Section \ref{Section:CMRS}) and present
empirical results on a simulated robotic control problem (Section
\ref{Section:ResultsMultiTask}).

\section{BACKGROUND} \label{Section:Background}

In this section, we provide a brief overview of
\textbf{Bayesian Optimization} (BO). We refer to \citet{shahriari_taking_2016} for a recent more
extensive review of BO. BO can be applied to black-back optimization
problems, which can be framed as optimizing an objective function $f:
\mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal X \subset
\mathbb{R}^D$. In contrast to most  other black-box optimization methods, BO is
a global method which makes use of all historic evaluations of $f(\mathbf{x})$
rather than using only a subset of the history for approximating a local
gradient or Hessian. For this, BO maintains a \emph{probabilistic model} for
$f(\mathbf{x})$, typically a Gaussian process \citep[GP,][]{rasmussen_gaussian_2006}, and uses this model for deciding
at which $\mathbf{x}_{n+1}$ the function $f$ will be evaluated next.

Assume we have already observed $n$ datapoints $\mathcal{D}_n=\{(\mathbf{x}_i,
y_i)\}_{i=1}^n$. The choice of the next query point $\mathbf{x}_{n+1}$ is based
on a utility function over the GP posterior, the so-called \emph{acquisition
function} $a: \mathcal X \to \mathbb{R}$, via $\mathbf{x}_{n+1}=
\arg\max_\mathbf{x} a(\mathbf{x})$. Since the maximum of the acquisition
function cannot be computed directly, a global optimizer is typically
used to determine $\mathbf{x}_{n+1}$. A common strategy
is to use
DIRECT \citep{jones_lipschitzian_1993} to find the approximate global maximum,
followed by L-BFGS \citep{byrd_limited-memory_1995} to refine it.

The first class of acquisition functions are \emph{optimistic policies} such as
the upper confidence bound (UCB) acquisition function. $a_{UCB}$ aims at minimizing the regret during the course of BO and has the form $$a_{UCB}(\mathbf{x};
\mathcal{D}_n) = \mu_{n}(\mathbf{x}) + \kappa_n \sigma_{n}(\mathbf{x}),$$ where
$\kappa_n$ is a tunable parameter which balances exploitation ($\kappa_n = 0$) and
exploration ($\kappa_n \gg 0$), and $\mu_{n}$ and $\sigma_{n}$ denote mean and
standard deviation of the GP at $\mathbf{x}$, respectively.
\citet{srinivas_gaussian_2010} proposed GP-UCB, which entails a specific schedule for $\kappa_n$ that yields provable cumulative regret bounds.

The second class of acquisition functions are \emph{improvement-based policies}, such as the probability of improvement \citep[PI,][]{kushner_new_1964} over the current best value, which can be calculated in closed-form for a GP model:
$$a_{PI}(\mathbf{x}; \mathcal{D}_n) := \mathbb{P}[f(\mathbf{x}) > \tau] = \Phi(\gamma(\mathbf{x})),$$
where $\gamma(x) = (\mu_n(\mathbf{x}) - \tau) / \sigma_n(x)$, $\Phi(\cdot)$ denotes the cumulative distribution function of the
standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max y_i$.
Since PI is known to exploit quite aggressively \cite{jones_taxonomy_2001}, a more popular
alternative is the \emph{expected improvement} \citep[EI,][]{mockus_application_1978} over the
current best value, which can again be computed in closed form for a GP model:
\begin{equation*}
\begin{split}
 a_{EI}(\mathbf{x}; \mathcal{D})
  & := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)] \\
  &  = \sigma_n(\mathbf{x})\left(\gamma(\mathbf{x})\Phi(\gamma(\mathbf{x})) + \phi(\gamma(\mathbf{x}))\right),
\end{split}
\end{equation*}
where $\phi(\cdot)$ denotes the standard Gaussian density function.

The third class of acquisition functions are \emph{information-based policies},
which entail Thompson sampling and entropy search
\citep[ES,][]{villemonteix_informational_2008, hennig_entropy_2012,hernandez-lobato_predictive_2014}.
Let $p_\star(x \vert \mathcal{D}_n)$ denote the
posterior distribution of the unknown optimizer $\mathbf{x}^\star = \arg\max_{\mathbf{x} \in \mathcal{X}} f(\mathbf{x})$  after
observing $\mathcal{D}_n$. The objective of ES is to select the query point that
results in the maximal reduction in the differential entropy of $p_\star$. More
formally, the entropy search acquisition function is defined as
$$ a_{ES}(\mathbf{x}, \mathcal{D}_n)
  = H(\mathbf{x}^\star \vert \mathcal{D}_n) - \mathbb{E}_{y \vert \mathbf{x}, \mathcal{D}_n}
    [H(\mathbf{x}^\star \vert \mathcal{D}_n \cup \{(\mathbf{x}, y))],$$
where $H(\mathbf{x}^\star \vert \mathcal{D}_n)$ denotes the differential entropy
of $p_\star(x \vert \mathcal{D}_n)$ and the expectation is with respect to the
predictive distribution of the GP at $\mathbf{x}$, which is a normal
distribution $y \sim \mathcal{N}(\mu_{n}(\mathbf{x}), \sigma_{n}^2(\mathbf{x}) +
\sigma^2)$. Computing $a_{ES}$ directly is intractable for continuous spaces
$\mathcal{X}$; prior work has discretized $\mathcal{X}$ and used either Monte
Carlo sampling \cite{villemonteix_informational_2008} or expectation propagation
\cite{hennig_entropy_2012}. While the former may require many Monte Carlo
samples to reduce variance, the latter incurs a run time that is quartic in the
number of representer points used in the discretization of $p_\star$. An
alternative formulation is obtained by exploiting the symmetric property of the
mutual information, which allows rewriting the ES acquisition function as
$$ a_{PES}(\mathbf{x}, \mathcal{D}_n)
  = H(y \vert \mathcal{D}_n, \mathbf{x}) - \mathbb{E}_{\mathbf{x}^\star \vert \mathcal{D}_n}
    [H(y \vert \mathcal{D}_n, \mathbf{x}, \mathbf{x}^\star)].$$
This acquisition function is known as predictive entropy search
\citep[PES,][]{hernandez-lobato_predictive_2014}. PES can be approximated more
efficiently, does not require discretization, and has obtained empirical results
that are as least as good as discretized ES with expectation propagation. A further advantage of PES is that it allows a formal treatment of GP hyperparameters.

\textbf{Contextual Policy Search} (CPS)
denotes a model-free approach to reinforcement learning,
in which the (low-level) policy $\pi_\mathbf{\theta}$ is parametrized by a vector
$\mathbf{\theta}$. The choice of $\mathbf{\theta}$ is governed by an upper-level policy
$\pi_{u}$. For generalizing learned policies to multiple tasks,
the task is characterized
by a context vector $\mathbf{s}$ and the upper-level policy
$\pi_{u}(\mathbf{\theta}\vert \mathbf{s})$ is conditioned on the respective
context. The objective of CPS is to learn
$\pi_{u}$ such that the expected return $J$ over all contexts is
maximized, with $J = \int_s p(\mathbf{s}) \int_\mathbf{\theta}
\pi_{u}(\mathbf{\theta}\vert \mathbf{s}) R(\mathbf{\theta}, \mathbf{s}) \D{\mathbf{\theta}
} \D{\mathbf{s}}$. Here, $p(\mathbf{s})$ is the distribution over contexts and
$R(\mathbf{\theta}, \mathbf{s})$ is the expected return when executing the low
level policy with parameter $\mathbf{\theta}$ in context $\mathbf{s}$. We refer to
\citet{deisenroth_survey_2013} for a recent overview of (contextual) policy
search approaches in robotics.

\section{MINIMUM REGRET SEARCH} \label{Section:MRS}

While information-based policies for Bayesian optimization such as ES and PES
have performed very well empirically, their internal objective of minimizing
the uncertainty in the location of the optimizer $\mathbf{x}^\star$, i.e.,
minimizing the differential entropy of $p_\star$, is actually different (albeit
related) to the common external objective of minimizing the immediate regret of
$\mathbf{\tilde x}_N$, the recommendation of BO for $\mathbf{x}^\star$ after $N$
trials, where we define the immediate regret of $\mathbf{\tilde x}_N$ as
$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$.

Clearly, $\mathbf{x}^\star$ has zero and thus minimum immediate regret, but a query that
results in the maximal decrease in $H(\mathbf{x}^\star)$ is not necessarily the
one that also results in the maximal decrease in the expected immediate regret
as we will discuss in Section \ref{Section:MRS_Illustration}. In this section, we propose \emph{minimum
regret search} (MRS), which explicitly aims at minimizing the expected immediate
regret.

\subsection{Formulation}
Let $X \subset \mathcal{R}^D$ be some bounded domain and $f: \mathcal{X} \mapsto
\mathbb{R}$ be a function. We are interested in finding the maximum
$\mathbf{x}^\star$ of $f$ on $\mathcal{X}$. Let there be a probability measure
$p(f)$ over the space of functions $f: \mathcal{X} \mapsto \mathbb{R}$, such as
a GP. Based on this $p(f)$, we would ultimately like to
select an $\mathbf{\tilde x}$ which has minimum immediate regret
$R_f(\mathbf{\tilde x})$. We define the expected immediate regret ER of
selecting parameter $\mathbf{x}$ under $p(f)$ as follows:
$$\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
x})]$$
The minimizer $\mathbf{\tilde x}$ of the expected immediate regret under fixed $p(f)$ can be determined efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$. However, in general, $p(f)$ depends on data and it is desirable to select the data such that $\text{ER}$ is also minimized with regard to the resulting $p(f)$.

In $N$-step minimum regret search (MRS), we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
$X^q_N=\{\mathbf{x}^q_1, \dots, \mathbf{x}^q_N\}$ for which we evaluate $y_n = f(\mathbf{x}^q_n) +
\epsilon$ to obtain $\mathcal{D}_N = \{\mathbf{x}^q_n, y_n\}_{n=1}^N$. Based on this, MRS
estimates $p_N(f) = p(f \vert \mathcal{D}_N)$  and recommends parameters
$\mathbf{\tilde x}_N$ as the estimate of $\mathbf{x}^\star$ such that the
expected regret under $p_N$ is minimized, i.e., $\mathbf{\tilde x}_N = \arg\min_\mathbf{x}
\text{ER}(p_N)(\mathbf{x})$.
 In general, we are interested in choosing a
sequence $X^q_N$ such that we minimize
$\text{ER}(p_N)(\mathbf{\tilde x}_N)$ with respect to the resulting $p_N$ (note that both $p_N$ and $\mathbf{\tilde x}_N$ depend on $X^q_N$).

As choosing the optimal sequence $X^q_N$ at once is intractable, we follow the
common approach in BO and select $\mathbf{x}^q_n$
sequentially in a myopic way. However, as $\mathbf{\tilde x}_N$ itself depends
on $\mathcal{D}_N$ and is thus unknown for $n < N$, we have to use proxies for it based on the currently
available subset $\mathcal{D}_n \subset \mathcal{D}_N$.  One simple choice for a proxy is to use
the point which has minimal expected immediate regret under $p_n(f) =
p(f \vert \mathcal{D}_n)$, i.e.,
$\mathbf{\tilde x} = \arg\min_\mathbf{x} \text{ER}(p_n)(\mathbf{x})$.
%Based on this, we define the one-step
%(myopic) expected regret reduction with respect to a given $p(f)$ when
%evaluating the function at $\mathbf{x}^q$.
Let us denote the updated
probability measure on $f$ after performing a query at $\mathbf{x}^q$ and
observing the function value $y=f(\mathbf{x}^q) + \epsilon$ by
$p^{[\mathbf{x}^q, y]}_n = p(f\vert \mathcal{D}_n \cup \{\mathbf{x}^q, y\})$.
We define the acquisition function MRS$^{\text{point}}$ as the expected reduction of the minimum expected regret for a query at
$\mathbf{x}^q$, i.e.,
\begin{equation*}
\begin{split}
a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
    & = \min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x}) \\
     &- \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})],
\end{split}
\end{equation*}
where the expectation is with
respect to $p_n(f)$'s predictive distribution at $\mathbf{x}^q$ and we drop the
implicit dependence on $p_n(f)$ in the notation of $a_{\text{MRS}^{\text{point}}}$.
The next query point $\mathbf{x}^q_{n+1}$ would thus be selected as the maximizer of
$a_{\text{MRS}^{\text{point}}}$.

One potential drawback of MRS$^{\text{point}}$, however,  is that it does not account for
the inherent uncertainty about $\mathbf{\tilde x}_N$. Alternatively, we propose using
the measure $p^\star_{\mathcal{D}_n} = p^\star(\mathbf{x} \vert \mathcal{D}_n)$ as defined in
entropy search (see Section \ref{Section:Background}) as proxy for $\mathbf{\tilde x}_N$.
%Let us denote the corresponding measure on $p^{[\mathbf{x}^q, y]}_n(f)$ by
%$p^\star_{n,\mathbf{x}^q, y}(\mathbf{\tilde x})$.
We denote the resulting acquisition function by MRS and define it analogously to $a_{\text{MRS}^{\text{point}}}$:
\begin{equation*}
\begin{split}
a_{\text{MRS}}(\mathbf{x}^q)
   & = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}[\text{ER}(p_n)(\mathbf{\tilde x})] \\
      & - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[
          \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n \cup \{(\mathbf{x}^q, y)\}}}[
             \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]].
\end{split}
\end{equation*}

MRS can thus be seen as a more Bayesian treatment, where we marginalize our
uncertainty about $\mathbf{\tilde x}_N$, while MRS$^\text{points}$ is more akin
to a point-estimate since we use a single point (the minimizer of the expected immediate regret)
as proxy for $\mathbf{\tilde x}_N$.

\subsection{Approximation}
Since several quantities in MRS cannot be computed in closed form, we
resort to similar discretizations and approximations as proposed for entropy search by \citet{hennig_entropy_2012}. We
focus here on sampling based approximations; for an alternative way of approximating $\mathbb{E}_{p(f)}$ based on
expectation propagation, we refer to \citet{hennig_entropy_2012}.

\begin{figure*}
\centering
\includegraphics{regret_illustration}
\includegraphics{acq_comparison}
\caption{(Left) Illustration of GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on the right-hand side). (Right) Illustration of GP posterior and different acquisition function. Absolute values have been normalized such that the mean value of an acquisition function is $0.5$. Best seen in color.}
\label{fig:MRS_illustration}
\end{figure*}

Firstly, we approximate $\mathbb{E}_{p(f)}$ by taking $n_f$ Monte Carlo samples
from $p(f)$, which is straightforward in the case of GPs.
Secondly, we approximate $\mathbb{E}_{y \vert p(f), \mathbf{x}^q}$  by taking
$n_y$ Monte Carlo samples from $p(f)$'s predictive distribution at
$\mathbf{x}_q$. And thirdly, we discretize $p^\star$ to a finite set of $n_r$
representer points chosen from a non-uniform measure, which turns
$\mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}$ in the definition of
$\text{MRS}(\mathbf{x}^q)$ into a weighted sum. The discretization of $p^\star$ is discussed by
\citet{hennig_entropy_2012} in detail; we select the representer points as
follows: for each representer point, we sample $250$ candidate points uniform
randomly from $\mathcal{X}$ and select the representer point by Thompson
sampling from $p(f)$ on the candidate points. Moreover, estimating $p^\star_n$ on the
representer points is relatively cheap as we can reuse the samples used for approximating $\mathbb{E}_{p(f)}$.

The resulting estimate of $a_{\text{MRS}}$ would have high variance and would require $n_f$ to be
chosen relatively large; however, we can reduce the variance considerably by using
common random numbers \citep{kahn_methods_1953} in the estimation of
$\text{ER}(p)(\mathbf{x})$ for different $p(f)$.

\subsection{Illustration} \label{Section:MRS_Illustration}

Figure \ref{fig:MRS_illustration} presents an illustration of different
acquisition functions on a simple one-dimensional target function. The left
graphic shows a hypothetical GP posterior (illustrated by its mean and standard
deviation) for length scale $l=0.75$, and the resulting probability of $\mathbf{x}$
being the optimum of $f$ denoted by $p^\star$.
Moreover, the expected immediate regret of selecting $\mathbf{x}$ denoted by
$\text{ER}(\mathbf{x})$ is shown. The minimum of $\text{ER}(\mathbf{x})$ and the maximum
of $p^\star$ are both at $\mathbf{\tilde x}=1.5$. The expected regret of $\mathbf{\tilde x}$
is approximately $\text{ER}(\mathbf{\tilde x}) = 0.07$. We plot $\mathbb{E}[\max(f(\mathbf{x}) -
f(\mathbf{\tilde x}), 0)]$ additionally to shed some light onto situations in which $
\mathbf{\tilde x} = 1.5$ would incur a significant regret: this quantity shows that most of the
expected regret of $\mathbf{\tilde x}$ stems from situations where the ``true''
optimum is located at $\mathbf{x} \geq 3.5$. This can be explained by the
observation that this area has high uncertainty and is at the same time largely
uncorrelated with $\mathbf{\tilde x} = 1.5$ because of the small length-scale of the GP.

The right graphic compares different acquisition functions for $n_f = 1000$,
$n_r=41$, $n_y = 11$, and fixed representer points.  Since the assumed GP is noise-free, the
acquisition-value of any parameter that has already been evaluated is approximately $0$.  The acquisition functions differ considerably in
their global shape: EI becomes large for areas with close-to-maximal predicted mean or with high uncertainty.
 ES becomes large for parameters which are informative with regard to most of the
probability mass of $p^\star$, i.e., for $\mathbf{x}^q \in [0.5, 3.0]$.  In contrast
MRS$^\text{point}$ becomes maximal for $\mathbf{x}^q \approx 4.0$. This can be
explained as follows: according to the current GP posterior, MRS$^\text{point}$ selects $\mathbf{\tilde x} = 1.5$. As shown in the Figure \ref{fig:MRS_illustration} (left),
most of the expected regret for this value of $\mathbf{\tilde x}$ stems from scenarios
where the true optimum would be at $\mathbf{x} \geq 3.5$. Thus, sampling in this
parameter range can reduce the expected regret considerably---either by confirming that the true value of $f(\mathbf{x})$ on $\mathbf{x} \geq 3.5$ is actually as small as expected or by switching $\mathbf{\tilde x}_{n+1}$ to this area if $f(\mathbf{x})$ turns out to be large. The maximum of MRS
is similar to MRS$^\text{point}$. However, since it also takes the whole measure
$p^\star$ into account, its acquisition surface is smoother in general; in particular, it assigns a larger value to regions such as $\mathbf{x}^q
\approx 3.0$, which do not cause regret for $\mathbf{\tilde x} = 1.5$ but for
alternative choices such as $\mathbf{\tilde x} = 4.0$.

Why does ES not assign a large acquisition value to $\mathbf{x}^q \geq 3.0$?
This is because ES does not take into account the correlation of different
(representer) points under $p(f)$. This, however, would be desirable as, e.g.,
reducing uncertainty regarding optimality among two highly correlated points
with large $p^\star$ (for instance $\mathbf{x}_1 = 1.5$ and $\mathbf{x}_2 =
1.55$ in the example) will not change the expected regret considerably since
both points will have nearly identical value under all $f \sim p(f)$. On the
other hand, the value of two points which are nearly uncorrelated under $p(f)$ and have non-zero $p^\star$ such as
$\mathbf{x}_1$ and $\mathbf{x}_3 = 4.0$ might differ considerably under
different $f \sim p(f)$ and choosing the wrong one as $\mathbf{\tilde x}$ might
cause considerable regret. Thus, identifying which of the two is actually
better would reduce the regret considerably. This is exactly why MRS assigns large value to $\mathbf{x}^q \approx 4.0$.

\section{MULTI-TASK MINIMUM REGRET SEARCH} \label{Section:CMRS}

Several extensions of Bayesian optimization for multi-task learning have been
proposed, both for discrete set of tasks \citep{krause_contextual_2011}
and for continuous set of tasks
\cite{metzen_active_2015}. Multi-task BO has been demonstrated to learn
efficiently about a set of discrete tasks concurrently
\cite{krause_contextual_2011}, to allow transferring knowledge learned on
cheaper tasks to more expensive tasks \cite{swersky_multi-task_2013}, and to
yield state-of-the-art performance on low-dimensional contextual policy search
problems \cite{metzen_bayesian_2015}, in particular when combined with active
learning \cite{metzen_active_2015}. In this section, we focus on multi-task BO
for a continuous set of tasks; a similar extension for discrete multi-task
learning would be straightforward.

A continuous set of tasks is encountered for instance when applying BO to
contextual policy search (see Section \ref{Section:Background}). We follow the
formulation of BO-CPS \cite{metzen_bayesian_2015} and adapt it for MRS were
required. In BO-CPS, the set of tasks is encoded in a context vector $\mathbf{s}
\in \mathcal{S}$ and BO-CPS learns a (non-parametric) upper-level policy $\pi_{u}$
which selects for a given context $\mathbf{s}$ the parameters $\mathbf{\theta}
\in \mathcal{X}$ of the low-level policy $\pi_\theta$. The unknown function $f$
corresponds to the expected return $R(\mathbf{\theta}, \mathbf{s})$ of executing
a low-level policy with parameters $\mathbf{\theta}$ in context $\mathbf{s}$.
Thus, the probability measure $p(f)$ (typically a GP) is defined over functions
$f: \mathcal{X} \times \mathcal{S} \mapsto \mathbb{R}$ on the joint
parameter-context space. The probability measure is conditioned on the trials performed so
far, i.e., $p_n(f) = p(f \vert \mathcal{D}_n)$ with $\mathcal{D}_n =
\{((\theta_i, s_i), r_i)\}_{i=1}^n$ for $r_i = R(\mathbf{\theta}_i, \mathbf{s}_i)$. Since $p_n$ is defined over the joint
parameter and context space, experience collected in one context is naturally
generalized to similar contexts.

In passive BO-CPS on which we focus here (please refer to
\citet{metzen_active_2015} for an active learning approach), the context (task)
$\mathbf{s}_n$ of a trial is determined externally according to $p(\mathbf{s})$,
and BO-CPS selects the parameter $\mathbf{\theta}_n$ by conditioning $p(f)$ on
$\mathbf{s}=\mathbf{s}_n$ and finding the maximum of the acquisition function
$a$ for fixed $\mathbf{s}_n$, i.e., $\mathbf{\theta}_n =
\arg\max_\mathbf{\theta} a(\mathbf{\theta}, \mathbf{s}_n)$. Acquisition
functions such as PI and EI are not easily generalized to multi-task problems as they are
defined relative to an incumbent $\tau$, which is typically the best function
value observed so far in a task. Since there are infinitely many tasks and no
task is visited twice with high probability, the notion of an incumbent is not
directly applicable.  In contrast, the acquisition functions GP-UCB
\cite{srinivas_gaussian_2010} and ES \cite{metzen_bayesian_2015} have been extended
straightforwardly and the same approach applies also to MRS.

\section{EXPERMENTS}

\subsection{Synthetic Single-Task Benchmark} \label{Section:ResultsSingleTask}

In the first experiment, we conduct a similar analysis as \citet[Section
3.1]{hennig_entropy_2012}: we compare different algorithms on a number of
single-task functions sampled from a generative model, namely from the same GP-based model
that is used by the optimization internally as surrogate model. This precludes
model-mismatch issues and unwanted bias which could be introduced by resorting
to common hand-crafted test functions. More specifically, we choose the
parameter space to be the 2-dimensional unit domain $\mathcal{X} = [0, 1]^2$ and generate test
functions by sampling $250$ function values jointly from a GP with an isotropic RBF kernel
of length scale $l = 0.1$ and unit signal variance. A GP is
fitted to these function values and the resulting posterior mean is used as the
test function. Moreover, Gaussian noise with standard deviation $\sigma =
10^{-3}$ is added to each observation. All algorithms were tested on the same
set of $250$ test functions, and we used $n_f=1000$, $n_r=25$, and $n_y=51$.
We do not provide error-bars on the estimates as the data sets have no parametric distribution. However, we provide additional histograms on the regret distribution.

\begin{figure*}
\centering
\includegraphics[width=.9\textwidth]{empirical_comparison}
\includegraphics[width=.9\textwidth]{hist}
\caption{(Top) Median and mean immediate regret over $250$ repetitions for different acquisition functions. Shown is the immediate regret that would have been obtained if BO would have been stopped after $N$ trials.
 (Bottom) Histogram of the immediate regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
\label{fig:empirical_comparison}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=.9\textwidth]{es_analysis}
\caption{Illustration of acquisition functions on a target function for
100 given samples and 25 representer points; darker areas correspond to larger values. ES focuses on sampling in areas with high density of $p^\star$ (many representer points), while MRS focuses on unexplored areas that are populated by representer points (non-zero $p^\star$).
}
\label{fig:es_analysis}
\end{figure*}

Figure \ref{fig:empirical_comparison} summarizes the results: according to the
median of the immediate regret (top left), ES, MRS, and MRS$^{point}$ perform
nearly identical, while EI is about an order of magnitude worse. GP-UCB performs
even worse initially but surpasses EI eventually. PI performs the worst as it
exploits too aggressively. These results are roughly in correspondence with prior
results \cite{hennig_entropy_2012,hernandez-lobato_predictive_2014} on the same
task; note, however, that \citet{hernandez-lobato_predictive_2014} used a lower
noise level and thus, absolute values are not comparable. However, according to
the \emph{mean} immediate regret, the picture changes considerably (top right):
here, MRS, MRS$^{point}$, and EI perform roughly on par while ES is about an order of
magnitude worse. This can be explained by the distribution of the immediate
regrets (bottom): while the distributions are fairly non-normal for all
acquisition functions, there are considerably more runs with very high immediate
regret ($R_f(\mathbf{\tilde x}_N)>10^{-2}$) for ES (10) than for MRS (4) or EI (4).

We illustrate one such case where ES incurs high immediate regret in Figure
\ref{fig:es_analysis}. The same set of representer points has been used for ES and MRS.
While both ES and MRS assign a non-zero density $p^\star$
(representer points) to the area of the true optimum of the function
(bottom center), ES assigns high acquisition value only to areas with a high
density of $p^\star$ in order to further concentrate density in these areas.
Note that this is not due to discretization of $p^\star$ but because of ES'
objective, which is to learn about the precise location of the optimum, irrespective of
how much correlation their is between the representer points according to $p(f)$.
Thus, predictive entropy search \cite{hernandez-lobato_predictive_2014} would likely be affected by the
same deficiency. In contrast, MRS focuses first on areas which have not been
explored and have a non-zero $p^\star$, since those are areas with high expected
immediate regret (see Section \ref{Section:MRS_Illustration}). Accordingly, MRS is less likely to incur a high immediate regret. In summary, the MRS-based acquisition functions are the only
acquisition functions that perform well both according to the median and the
mean immediate regret; moreover, MRS performs slightly better than
MRS$^{point}$ and we will focus on MRS subsequently.

\subsection{Multi-Task Robotic Behavior Learning} \label{Section:ResultsMultiTask}

We present results in the simulated robotic control task used by
\citet{metzen_active_2015}, in which the robot arm COMPI \cite{COMPI} is used to
throw a ball at a target on the ground encoded in a two-dimensional context
vector. The target area is $\mathcal{S} = [1, 2.5]m \times [-1, 1]m$ and the robot arm is
mounted at the origin $(0, 0)$ of this coordinate system. Contexts are sampled uniform randomly from $\mathcal{S}$.
The low-level policy is a joint-space dynamical movement primitives
\citep[DMP,][]{ijspeert_dynamical_2013} with preselected start and goal angle
for each joint and all DMP weights set to 0. This DMP results in throwing a ball
such that it hits the ground close to the center of the target area. Adaptation
to different target positions is achieved by modifying the parameter
$\mathbf{\theta}$: the first component of $\mathbf{\theta}$ corresponds to the
execution time $\tau$ of the DMP, which determines how far the ball is thrown,
and the further components encode the final angle $g_i$ of the $i$-th joint.
We compare the learning performance for different number of controllable joints;
the not-controlled joints keep the preselect goal angles of the initial throw.
The limits on the parameter space are $g_i \in \left[-\frac{\pi}{2}, \frac{\pi}{2}\right]$ and $\tau \in \left[0.4, 2\right]$.

All approaches use a GP with anisotropic Mat{\'e}rn kernel for representing
$p(f)$. Since we focus on a ``pure exploration'' scenario
\cite{bubeck_pure_2009}, UCB's exploration parameter $\kappa$ is set to a
constant value of $5.0$. For MRS and ES, we use the same parameter values as in
the Section \ref{Section:ResultsSingleTask}, namely $n_f=1000$, $n_r=25$, and $n_y=51$. Moreover, we
add a ``greedy'' acquisition function, which always selects $\theta$ that
maximizes the mean of the GP for the given context (UCB with $\kappa=0$), and a
``random'' acquisition function that selects $\theta$ randomly. The return is
defined as $R(\mathbf{\theta}, \mathbf{s}) = -||\mathbf{s} - b_s||^2 - 0.01
\sum_t v_t^2$, where $b_s$ denotes the position hit by the ball, and $\sum_t
v_t^2$ denotes a penalty term on the sum of squared joint velocities during DMP
execution; both $b_s$ and $\sum_t v_t^2$ depend indirectly on $\mathbf{\theta}$.

\begin{figure*}
\centering
\includegraphics[width=.85\textwidth]{learning_curve}
\caption{Learning curves on the ball-throwing task for different acquisition functions and different number of controllable joints (first joint, first and second joint, and so on). Shown are mean and standard error of mean over $30$ repetitions of the greedy upper-level policy if learning would have been stopped after $N$ episodes.}
\label{fig:experiment}
\end{figure*}

Figure \ref{fig:experiment} summarizes the main results of the empirical
evaluation for different acquisition functions. Shown is the mean offline
performance of the upper-level policy at $16$ test contexts on a grid over the
context space. Selecting parameters randomly (``Random'') or greedily
(``Greedy'') during learning is shown as a baseline and indicates that
generalizing experience using a GP model alone does not suffice for quick
learning in this task. In general, performance when learning only the execution
time and the first joint is better than learning several joins at once. This is
because the execution time and first joint allow already adapting the throw to
different contexts \citep{metzen_bayesian_2015}; controlling more joints mostly
adds additional search dimensions. MRS and ES perform on par for controlling one
or two joints and outperform UCB. For higher-dimensional search spaces (three or
four controllable joints), MRS performs slightly better than ES ($p < 0.01$ after $200$ episodes for
a Wilcoxon signed-rank test). A potential reason for this might be the increasing number of areas with potentially high regret in higher dimensional spaces that may remain unexplored by ES; however, this hypothesis requires further investigation in the future.

\section{DISCUSSION AND CONCLUSION}

We have proposed MRS, a new class of acquisition functions for single- and multi-task
Bayesian optimization that is based on the principle of minimizing the expected
regret. We have compared MRS empirically to other acquisition functions on a
synthetic single-task optimization problem and a simulated multi-task robotic
control problem.  The results indicate that MRS performs favorably compared to the
other approaches and incurs less often a high regret than ES since its
objective is explicitly focused on minimizing the regret. An empirical
comparison with PES remains future work; since PES uses the same objective as ES
(minimizing $H(\mathbf{x}^\star)$), it will likely show the same deficit of
ignoring areas that have small probability $p^\star$ but could nevertheless cause a large
potential regret. On the other hand, PES allows a formal treatment
of GP hyperparameters and can be approximated more efficiently than ES or MRS.
Potential future research on approaches for addressing
GP hyperparameters and more efficient approximation techniques for MRS would thus be desirable. Additionally,
combining MRS with active learning as done for entropy search by
\citet{metzen_active_2015} would be interesting. Moreover, we consider MRS to
be a valuable addition to the set of base strategies in a portfolio-based BO
approach \cite{shahriari_entropy_2014}. On a more theoretical level, it would be interesting if formal regret bounds can be proven for MRS.

%\todo{}{Remove Acknowledgments for submission}
\paragraph{Acknowledgments}
This work was supported through two grants of the German Federal Ministry of Economics and Technology (BMWi, FKZ 50 RA 1216 and FKZ 50 RA 1217).

\bibliographystyle{icml2016}
\bibliography{literature}

\end{document}

### 2016-05-13 2016_ICML/cmrs.tex
Minor changes based on reviewer's remarks

@@
 expected immediate regret of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
-cases, MRS produces fewer outliers with high regret than ES. We provide empirical
+cases, MRS produces fewer outliers with high immediate regret than ES. We provide empirical
 results both for a synthetic single-task optimization problem as well as for a
@@
 function with a finite number of function evaluations. Instead, one often aims
-at finding a solution which has small regret with regard to the true optimum. BO
-aims at finding such a solution of minimum regret while  minimizing at the same
+at finding a solution which has small \emph{immediate regret} with regard to the true optimum, where 
+``immediate regret'' denotes the difference of function value of the selected solution to 
+true the optimal function value. BO
+aims at finding such a solution of minimum immediate regret while  minimizing at the same
 time the number of evaluations of the expensive target function. For this, BO
@@
 search-based approaches
-\cite{villemonteix_informational_2008, hennig_entropy_2012,hernandez-lobato_predictive_2014}, which aims at maximizing the information gain regarding
+\cite{villemonteix_informational_2008, hennig_entropy_2012,hernandez-lobato_predictive_2014}, 
+which aims at maximizing the information gain regarding
 the true optimum, has achieved state-of-the-art performance on a number of
@@
 This acquisition function is known as predictive entropy search
-\citep[PES,][]{hernandez-lobato_predictive_2014}. PES can be approximated more
-efficiently, does not require discretization, and has obtained empirical results
-that are as least as good as discretized ES with expectation propagation. A further advantage of PES is that it allows a formal treatment of GP hyperparameters.
+\citep[PES,][]{hernandez-lobato_predictive_2014}. PES does not require discretization
+and allows a formal treatment of GP hyperparameters.
 

### 2016-05-18 2016_ICML/cmrs.tex
Format corrections and some minor changes

@@
-\documentclass{article} % For LaTeX2e
+\documentclass[10pt,letterpaper]{article} % For LaTeX2e
 
@@
 
-\usepackage{umoline}
-%\newcommand{\todo}[2]{\Underline{#1}\textbf{ [\scriptsize TODO: #2] }}
-\newcommand{\todo}[2]{#1}
+\usepackage{times}
 
@@
 \icmlauthor{Jan Hendrik Metzen}{janmetzen@mailbox.org}
-\icmladdress{Universit{\"a}t Bremen, 28359 Bremen, Germany \&
+\icmladdress{Universit{\"a}t Bremen, 28359 Bremen, Germany \\
              Robert Bosch GmbH, 70442 Stuttgart, Germany}
@@
 at finding a solution which has small \emph{immediate regret} with regard to the true optimum, where 
-``immediate regret'' denotes the difference of function value of the selected solution to 
-true the optimal function value. BO
+``immediate regret'' denotes the difference of the true optimal function value 
+and the function value of the selected solution. BO
 aims at finding such a solution of minimum immediate regret while  minimizing at the same
@@
 \textbf{Bayesian Optimization} (BO). We refer to \citet{shahriari_taking_2016} for a recent more
-extensive review of BO. BO can be applied to black-back optimization
+extensive review of BO. BO can be applied to black-box optimization
 problems, which can be framed as optimizing an objective function $f:
@@
 \mathbb{R}^D$. In contrast to most  other black-box optimization methods, BO is
-a global method which makes use of all historic evaluations of $f(\mathbf{x})$
+a global method which makes use of all previous evaluations of $f(\mathbf{x})$
 rather than using only a subset of the history for approximating a local
@@
 \subsection{Formulation}
-Let $X \subset \mathcal{R}^D$ be some bounded domain and $f: \mathcal{X} \mapsto
+Let $\mathcal{X} \subset \mathcal{R}^D$ be some bounded domain and $f: \mathcal{X} \mapsto
 \mathbb{R}$ be a function. We are interested in finding the maximum

### 2016-05-18 2016_ICML/cmrs.tex
Adressing R3

@@
 Bayesian optimization \citep[BO,][]{shahriari_taking_2016} denotes a sequential,
-model-based, global approach for optimizing black-box functions that are
-non-convex, do not necessarily provide derivatives, are expensive to evaluate (either
-computationally, economically, or morally), and are potentially noisy. Under
+model-based, global approach for optimizing black-box functions. It is particularly well-suited for problems
+which are non-convex, do not necessarily provide derivatives, are expensive to evaluate (either
+computationally, economically, or morally), and can potentially be noisy. Under
 these conditions, there is typically no guarantee for finding the true optimum of the
@@
 ``immediate regret'' denotes the difference of the true optimal function value 
-and the function value of the selected solution. BO
-aims at finding such a solution of minimum immediate regret while  minimizing at the same
+and the function value of the ``solution'' selected by the algorithm after a finite number of function evaluations. BO
+aims at finding such a solution of small immediate regret while  minimizing at the same
 time the number of evaluations of the expensive target function. For this, BO
@@
 
-BO has been applied to a diverse set of problems, ranging from automatic  machine
-learning \cite{bergstra_algorithms_2011,snoek_practical_2012} over robotics
+BO has been applied to a diverse set of problems, ranging from hyperparameter optimization
+of machine learning models \cite{bergstra_algorithms_2011,snoek_practical_2012} over robotics
 \cite{calandra_bayesian_2015,lizotte_automatic_2007,kroemer_combining_2010,alonso_an_2015} to

### 2016-05-18 2016_ICML/cmrs.tex
Further changes based on comments from R§

@@
 $\mathbf{s}_n$ of a trial is determined externally according to $p(\mathbf{s})$, 
-and BO-CPS selects the parameter $\mathbf{\theta}_n$ by conditioning $p(f)$ on
+for which we assume a uniform distribution in this work.
+BO-CPS selects the parameter $\mathbf{\theta}_n$ by conditioning $p(f)$ on
 $\mathbf{s}=\mathbf{s}_n$ and finding the maximum of the acquisition function
@@
 test function. Moreover, Gaussian noise with standard deviation $\sigma =
-10^{-3}$ is added to each observation. All algorithms were tested on the same
+10^{-3}$ is added to each observation. The GP used as surrogate model in the optimizer employed the same 
+isotropic RBF kernel with fixed, identical hyperparameters. 
+In order to isolate effects of the different acquisition functions from effects of different
+recommendation mechanisms, we used the point which maximizes the GP posterior
+mean as recommendation $\mathbf{\tilde x}_N$ regardless of the employed acquisition function.
+All algorithms were tested on the same
 set of $250$ test functions, and we used $n_f=1000$, $n_r=25$, and $n_y=51$.
-We do not provide error-bars on the estimates as the data sets have no parametric distribution. However, we provide additional histograms on the regret distribution.
+We do not provide error-bars on the estimates as the data sets have no parametric distribution. 
+However, we provide additional histograms on the regret distribution.
 
@@
 \caption{(Top) Median and mean immediate regret over $250$ repetitions for different acquisition functions.
-Shown is the immediate regret that would have been obtained if BO would have been stopped after $N$ trials.
- (Bottom) Histogram of the immediate regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
+Shown is the immediate regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials, i.e., the point which maximizes the GP posterior
+mean. (Bottom) Histogram of the immediate regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
 \label{fig:empirical_comparison}
@@
 nearly identical, while EI is about an order of magnitude worse. GP-UCB performs
-even worse initially but surpasses EI eventually. PI performs the worst as it
+even worse initially but surpasses EI eventually\footnote{GP-UCB reaches 
+the same level of mean and median immediate regret  as MRS after $N=200$ steps 
+(in mean and median) with no significant difference  according to a Wilcoxon signed-rank test.}. 
+PI performs the worst as it
 exploits too aggressively. These results are roughly in correspondence with prior
@@
 All approaches use a GP with anisotropic Mat{\'e}rn kernel for representing
-$p(f)$. Since we focus on a ``pure exploration'' scenario
-\cite{bubeck_pure_2009}, UCB's exploration parameter $\kappa$ is set to a
+$p(f)$ and the kernel's length scales and signal variance are selected in each 
+BO iteration as point estimates using maximum marginal likelihood. Based on preliminary experiments,
+UCB's exploration parameter $\kappa$ is set to a
 constant value of $5.0$. For MRS and ES, we use the same parameter values as in

### 2016-05-19 2016_ICML/cmrs.tex
Changing conclusion to be more diplomatic about ES
Adding knowledge gradient to background

@@
 \end{equation*}
-where $\phi(\cdot)$ denotes the standard Gaussian density function.
+where $\phi(\cdot)$ denotes the standard Gaussian density function.  A
+generalization of EI is the \emph{knowledge gradient} factor \cite
+{frazier_knowledge-gradient_2009}, which can better handle noisy observations,
+which impede the estimation of the incumbent. The knowledge gradient requires
+defining a set $A_n$ from which one would choose the final solution.
 
@@
 ignoring areas that have small probability $p^\star$ but could nevertheless cause a large
-potential regret. On the other hand, PES allows a formal treatment
-of GP hyperparameters and can be approximated more efficiently than ES or MRS.
-Potential future research on approaches for addressing
+potential regret. On the other hand, in contrast to ES and MRS, PES allows a formal treatment
+of GP hyperparameters, which can make it more sample-efficient. Potential future research on approaches for addressing
 GP hyperparameters and more efficient approximation techniques for MRS would thus be desirable. Additionally,

### 2016-05-19 2016_ICML/cmrs.tex
Replacing "immediate regret" by "simple regret" and mentioning pure exploration setting

@@
 information gain with respect to the global maximum, MRS aims at minimizing the
-expected immediate regret of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
-cases, MRS produces fewer outliers with high immediate regret than ES. We provide empirical
+expected simple regret of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
+cases, MRS produces fewer outliers with high simple regret than ES. We provide empirical
 results both for a synthetic single-task optimization problem as well as for a
@@
 function with a finite number of function evaluations. Instead, one often aims
-at finding a solution which has small \emph{immediate regret} with regard to the true optimum, where 
-``immediate regret'' denotes the difference of the true optimal function value 
+at finding a solution which has small \emph{simple regret} \cite{bubeck_pure_2009}) with regard to the true optimum, where 
+simple regret denotes the difference of the true optimal function value 
 and the function value of the ``solution'' selected by the algorithm after a finite number of function evaluations. BO
-aims at finding such a solution of small immediate regret while  minimizing at the same
+aims at finding such a solution of small simple regret while  minimizing at the same
 time the number of evaluations of the expensive target function. For this, BO
@@
 the performance of sampling-based entropy search is not necessarily better
-than traditional and cheaper acquisition functions according to the mean immediate regret.
+than traditional and cheaper acquisition functions according to the mean simple regret.
 
 In this work, we propose minimum regret search (MRS), a novel acquisition
-function that explicitly aims at minimizing the expected immediate regret
+function that explicitly aims at minimizing the expected simple regret
 (Section \ref{Section:MRS}). MRS performs well according to both the mean and
@@
 minimizing the differential entropy of $p_\star$, is actually different (albeit
-related) to the common external objective of minimizing the immediate regret of
+related) to the common external objective of minimizing the simple regret of
 $\mathbf{\tilde x}_N$, the recommendation of BO for $\mathbf{x}^\star$ after $N$
-trials, where we define the immediate regret of $\mathbf{\tilde x}_N$ as
+trials, where we define the simple regret of $\mathbf{\tilde x}_N$ as
 $R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$.
 
-Clearly, $\mathbf{x}^\star$ has zero and thus minimum immediate regret, but a query that
+Clearly, $\mathbf{x}^\star$ has zero and thus minimum simple regret, but a query that
 results in the maximal decrease in $H(\mathbf{x}^\star)$ is not necessarily the
-one that also results in the maximal decrease in the expected immediate regret
+one that also results in the maximal decrease in the expected simple regret
 as we will discuss in Section \ref{Section:MRS_Illustration}. In this section, we propose \emph{minimum
-regret search} (MRS), which explicitly aims at minimizing the expected immediate
+regret search} (MRS), which explicitly aims at minimizing the expected simple
 regret.
@@
 a GP. Based on this $p(f)$, we would ultimately like to
-select an $\mathbf{\tilde x}$ which has minimum immediate regret
-$R_f(\mathbf{\tilde x})$. We define the expected immediate regret ER of
+select an $\mathbf{\tilde x}$ which has minimum simple regret
+$R_f(\mathbf{\tilde x})$. We define the expected simple regret ER of
 selecting parameter $\mathbf{x}$ under $p(f)$ as follows:
@@
 x})]$$
-The minimizer $\mathbf{\tilde x}$ of the expected immediate regret under fixed $p(f)$ can be determined efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.
+The minimizer $\mathbf{\tilde x}$ of the expected simple regret under fixed $p(f)$ can be determined efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.
 However, in general, $p(f)$ depends on data and it is desirable to select the data such that $\text{ER}$ is also minimized with regard to the resulting $p(f)$.
@@
 available subset $\mathcal{D}_n \subset \mathcal{D}_N$.  One simple choice for a proxy is to use
-the point which has minimal expected immediate regret under $p_n(f) =
+the point which has minimal expected simple regret under $p_n(f) =
 p(f \vert \mathcal{D}_n)$, i.e.,
@@
 uncertainty about $\mathbf{\tilde x}_N$, while MRS$^\text{points}$ is more akin
-to a point-estimate since we use a single point (the minimizer of the expected immediate regret)
+to a point-estimate since we use a single point (the minimizer of the expected simple regret)
 as proxy for $\mathbf{\tilde x}_N$.
@@
 being the optimum of $f$ denoted by $p^\star$.
-Moreover, the expected immediate regret of selecting $\mathbf{x}$ denoted by
+Moreover, the expected simple regret of selecting $\mathbf{x}$ denoted by
 $\text{ER}(\mathbf{x})$ is shown. The minimum of $\text{ER}(\mathbf{x})$ and the maximum
@@
 \includegraphics[width=.9\textwidth]{hist}
-\caption{(Top) Median and mean immediate regret over $250$ repetitions for different acquisition functions.
-Shown is the immediate regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials, i.e., the point which maximizes the GP posterior
-mean. (Bottom) Histogram of the immediate regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
+\caption{(Top) Median and mean simple regret over $250$ repetitions for different acquisition functions.
+Shown is the simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials, i.e., the point which maximizes the GP posterior
+mean. (Bottom) Histogram of the simple regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
 \label{fig:empirical_comparison}
@@
 
-Figure \ref{fig:empirical_comparison} summarizes the results: according to the
-median of the immediate regret (top left), ES, MRS, and MRS$^{point}$ perform
+Figure \ref{fig:empirical_comparison} summarizes the results for a pure
+exploration setting, where we are only interested in the quality of the
+algorithm's recommendation for the optimum after $N$ queries but not in the
+quality of the queries themselves:  according to the
+median of the simple regret (top left), ES, MRS, and MRS$^{point}$ perform
 nearly identical, while EI is about an order of magnitude worse. GP-UCB performs
 even worse initially but surpasses EI eventually\footnote{GP-UCB reaches 
-the same level of mean and median immediate regret  as MRS after $N=200$ steps 
+the same level of mean and median simple regret  as MRS after $N=200$ steps 
 (in mean and median) with no significant difference  according to a Wilcoxon signed-rank test.}. 
@@
 noise level and thus, absolute values are not comparable. However, according to
-the \emph{mean} immediate regret, the picture changes considerably (top right):
+the \emph{mean} simple regret, the picture changes considerably (top right):
 here, MRS, MRS$^{point}$, and EI perform roughly on par while ES is about an order of
-magnitude worse. This can be explained by the distribution of the immediate
+magnitude worse. This can be explained by the distribution of the simple
 regrets (bottom): while the distributions are fairly non-normal for all
-acquisition functions, there are considerably more runs with very high immediate
+acquisition functions, there are considerably more runs with very high simple
 regret ($R_f(\mathbf{\tilde x}_N)>10^{-2}$) for ES (10) than for MRS (4) or EI (4).
 
-We illustrate one such case where ES incurs high immediate regret in Figure
+We illustrate one such case where ES incurs high simple regret in Figure
 \ref{fig:es_analysis}. The same set of representer points has been used for ES and MRS.
@@
 explored and have a non-zero $p^\star$, since those are areas with high expected
-immediate regret (see Section \ref{Section:MRS_Illustration}). Accordingly, MRS is less likely to incur a high immediate regret. In summary, the MRS-based acquisition functions are the only
+simple regret (see Section \ref{Section:MRS_Illustration}). Accordingly, MRS is less likely to incur a high simple regret. In summary, the MRS-based acquisition functions are the only
 acquisition functions that perform well both according to the median and the
-mean immediate regret; moreover, MRS performs slightly better than
+mean simple regret; moreover, MRS performs slightly better than
 MRS$^{point}$ and we will focus on MRS subsequently.

### 2016-05-19 2016_ICML/cmrs.tex
Adding URL of code

@@
 
-In the first experiment, we conduct a similar analysis as \citet[Section
+In the first experiment\footnote{Source code for replicating the reported experiment
+is available under \url{https://github.com/jmetzen/bayesian_optimization}.}, 
+we conduct a similar analysis as \citet[Section
 3.1]{hennig_entropy_2012}: we compare different algorithms on a number of

### 2016-05-19 2016_ICML/cmrs.tex
Discussing bias in approximation section

@@
 randomly from $\mathcal{X}$ and select the representer point by Thompson
-sampling from $p(f)$ on the candidate points. Moreover, estimating $p^\star_n$ on the
-representer points is relatively cheap as we can reuse the samples used for approximating $\mathbb{E}_{p(f)}$.
+sampling from $p(f)$ on the candidate points. Moreover, estimating $p^\star_{\mathcal{D}_n}$ 
+on the representer points can be done relatively cheap by reusing the samples used 
+for approximating $\mathbb{E}_{p(f)}$, which incurs a small bias which had, however, a negligible 
+effect in preliminary experiments.
 

### 2016-05-19 2016_ICML/cmrs.tex
Restructuring introduction of Section 3.

@@
 While information-based policies for Bayesian optimization such as ES and PES
-have performed very well empirically, their internal objective of minimizing
+have performed very well empirically, we discuss in Section \ref{Section:MRS_Illustration} 
+that their internal objective of minimizing
 the uncertainty in the location of the optimizer $\mathbf{x}^\star$, i.e.,
@@
 results in the maximal decrease in $H(\mathbf{x}^\star)$ is not necessarily the
-one that also results in the maximal decrease in the expected simple regret
-as we will discuss in Section \ref{Section:MRS_Illustration}. In this section, we propose \emph{minimum
-regret search} (MRS), which explicitly aims at minimizing the expected simple
+one that also results in the maximal decrease in the expected simple regret. 
+In this section, we propose \emph{minimum regret search} (MRS), 
+which explicitly aims at minimizing the expected simple
 regret.

### 2016-05-23 2016_ICML/cmrs.tex
Changes after final proof-reading

@@
 \icmladdress{Universit{\"a}t Bremen, 28359 Bremen, Germany \\
-             Robert Bosch GmbH, 70442 Stuttgart, Germany}
+             Corporate Research, Robert Bosch GmbH, 70442 Stuttgart, Germany}
 %\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
@@
 function with a finite number of function evaluations. Instead, one often aims
-at finding a solution which has small \emph{simple regret} \cite{bubeck_pure_2009}) with regard to the true optimum, where 
+at finding a solution which has small \emph{simple regret} \cite{bubeck_pure_2009} with regard to the true optimum, where 
 simple regret denotes the difference of the true optimal function value 
@@
 
-Assume we have already observed $n$ datapoints $\mathcal{D}_n=\{(\mathbf{x}_i,
+Assume we have already queried $n$ datapoints and observed their (noisy) function values $\mathcal{D}_n=\{(\mathbf{x}_i,
 y_i)\}_{i=1}^n$. The choice of the next query point $\mathbf{x}_{n+1}$ is based
@@
 where $\gamma(x) = (\mu_n(\mathbf{x}) - \tau) / \sigma_n(x)$, $\Phi(\cdot)$ denotes the cumulative distribution function of the
-standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max y_i$.
+standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max_i y_i$.
 Since PI is known to exploit quite aggressively \cite{jones_taxonomy_2001}, a more popular
@@
 $\pi_{u}(\mathbf{\theta}\vert \mathbf{s})$ is conditioned on the respective
-context. The objective of CPS is to learn
+context. The objective of CPS is to learn the upper-level policy
 $\pi_{u}$ such that the expected return $J$ over all contexts is
-maximized, with $J = \int_s p(\mathbf{s}) \int_\mathbf{\theta}
+maximized, where $J = \int_s p(\mathbf{s}) \int_\mathbf{\theta}
 \pi_{u}(\mathbf{\theta}\vert \mathbf{s}) R(\mathbf{\theta}, \mathbf{s}) \D{\mathbf{\theta}
@@
 
-While information-based policies for Bayesian optimization such as ES and PES
-have performed very well empirically, we discuss in Section \ref{Section:MRS_Illustration} 
-that their internal objective of minimizing
+Information-based policies for Bayesian optimization such as ES and PES
+have performed well empirically. However, as we discuss in Section \ref{Section:MRS_Illustration},
+their internal objective of minimizing
 the uncertainty in the location of the optimizer $\mathbf{x}^\star$, i.e.,
 minimizing the differential entropy of $p_\star$, is actually different (albeit
-related) to the common external objective of minimizing the simple regret of
+related) to the common external objective of minimizing the \emph{simple regret} of
 $\mathbf{\tilde x}_N$, the recommendation of BO for $\mathbf{x}^\star$ after $N$
-trials, where we define the simple regret of $\mathbf{\tilde x}_N$ as
+trials. We define the simple regret of $\mathbf{\tilde x}_N$ as
 $R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$.
@@
 x})]$$
-The minimizer $\mathbf{\tilde x}$ of the expected simple regret under fixed $p(f)$ can be determined efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.
+The minimizer $\mathbf{\tilde x}$ of the expected simple regret under fixed $p(f)$ can be approximated efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.
 However, in general, $p(f)$ depends on data and it is desirable to select the data such that $\text{ER}$ is also minimized with regard to the resulting $p(f)$.
 
-In $N$-step minimum regret search (MRS), we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
+In $N$-step Bayesian optimization, we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
 $X^q_N=\{\mathbf{x}^q_1, \dots, \mathbf{x}^q_N\}$ for which we evaluate $y_n = f(\mathbf{x}^q_n) +
@@
 sequence $X^q_N$ such that we minimize
-$\text{ER}(p_N)(\mathbf{\tilde x}_N)$ with respect to the resulting $p_N$ (note that both $p_N$ and $\mathbf{\tilde x}_N$ depend on $X^q_N$).
+$\min_\mathbf{x} \text{ER}(p_N)(\mathbf{x})$ with respect to the resulting $p_N$.
 
@@
 One potential drawback of MRS$^{\text{point}}$, however,  is that it does not account for
-the inherent uncertainty about $\mathbf{\tilde x}_N$. Alternatively, we propose using
+the inherent uncertainty about $\mathbf{\tilde x}_N$. To address this shortcoming, we propose using
 the measure $p^\star_{\mathcal{D}_n} = p^\star(\mathbf{x} \vert \mathcal{D}_n)$ as defined in
@@
 MRS can thus be seen as a more Bayesian treatment, where we marginalize our
-uncertainty about $\mathbf{\tilde x}_N$, while MRS$^\text{points}$ is more akin
+uncertainty about $\mathbf{\tilde x}_N$, while MRS$^\text{point}$ is more akin
 to a point-estimate since we use a single point (the minimizer of the expected simple regret)
@@
 
-Why does ES not assign a large acquisition value to $\mathbf{x}^q \geq 3.0$?
+Why does ES not assign a large acquisition value to query points $\mathbf{x}^q \geq 3.0$?
 This is because ES does not take into account the correlation of different
@@
 nearly identical, while EI is about an order of magnitude worse. GP-UCB performs
-even worse initially but surpasses EI eventually\footnote{GP-UCB reaches 
-the same level of mean and median simple regret  as MRS after $N=200$ steps 
+even worse initially but surpasses EI eventually\footnote{GP-UCB would reach 
+the same level of mean and median simple regret as MRS eventually after $N=200$ steps 
 (in mean and median) with no significant difference  according to a Wilcoxon signed-rank test.}. 
@@
 We have proposed MRS, a new class of acquisition functions for single- and multi-task
-Bayesian optimization that is based on the principle of minimizing the expected
+Bayesian optimization that is based on the principle of minimizing the expected simple
 regret. We have compared MRS empirically to other acquisition functions on a
@@
 control problem.  The results indicate that MRS performs favorably compared to the
-other approaches and incurs less often a high regret than ES since its
+other approaches and incurs less often a high simple regret than ES since its
 objective is explicitly focused on minimizing the regret. An empirical

### 2016-05-23 2016_ICML/cmrs.tex
Revising Section 3.1

@@
 x})]$$
-The minimizer $\mathbf{\tilde x}$ of the expected simple regret under fixed $p(f)$ can be approximated efficiently in the case of a GP since it is identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.
-However, in general, $p(f)$ depends on data and it is desirable to select the data such that $\text{ER}$ is also minimized with regard to the resulting $p(f)$.
 
-In $N$-step Bayesian optimization, we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
-$X^q_N=\{\mathbf{x}^q_1, \dots, \mathbf{x}^q_N\}$ for which we evaluate $y_n = f(\mathbf{x}^q_n) +
-\epsilon$ to obtain $\mathcal{D}_N = \{\mathbf{x}^q_n, y_n\}_{n=1}^N$. Based on this, MRS
-estimates $p_N(f) = p(f \vert \mathcal{D}_N)$  and recommends parameters
-$\mathbf{\tilde x}_N$ as the estimate of $\mathbf{x}^\star$ such that the
-expected regret under $p_N$ is minimized, i.e., $\mathbf{\tilde x}_N = \arg\min_\mathbf{x}
+In $N$-step BO, we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
+$X^q_N=\{\mathbf{x}^q_1, \dots, \mathbf{x}^q_N\}$ for which we evaluate $y_i = f(\mathbf{x}^q_i) +
+\epsilon$ to obtain $\mathcal{D}_N = \{\mathbf{x}^q_i, y_i\}_{i=1}^N$. Based on this, 
+ $p_N(f) = p(f \vert \mathcal{D}_N)$ is estimated and a point
+$\mathbf{\tilde x}_N$ is recommended as the estimate of $\mathbf{x}^\star$ such that the
+expected simple regret under $p_N$ is minimized, i.e., $\mathbf{\tilde x}_N = \arg\min_\mathbf{x}
 \text{ER}(p_N)(\mathbf{x})$.
- In general, we are interested in choosing a
-sequence $X^q_N$ such that we minimize
-$\min_\mathbf{x} \text{ER}(p_N)(\mathbf{x})$ with respect to the resulting $p_N$.
+The minimizer $\mathbf{\tilde x}_N$ of the expected simple regret under fixed
+$p(f)$ can be approximated efficiently in the case of a GP since it is
+identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.
 
+However, in general, $p(f)$ depends on data and it is desirable to select the data such
+that $\text{ER}$ is also minimized with regard to the resulting $p(f)$.
+We are thus interested in choosing a
+sequence $X^q_N$ such that we minimize the expected simple regret of $\mathbf{\tilde x}_N$ with respect to the $p_N$, where $p_N$ depends on $X^q_N$ and the (potentially noisy) observations $y_i$.
 As choosing the optimal sequence $X^q_N$ at once is intractable, we follow the

### 2016-05-23 2016_ICML/appendix.tex
Adding supplementary material on model-mismatch

\section{Synthetic Single-Task Benchmark with Model Mismatch}

\begin{figure*}
\centering
\includegraphics[width=.9\textwidth]{empirical_comparison_mm}
\includegraphics[width=.9\textwidth]{hist_mm}
\caption{(Top) Median and mean simple regret over $250$ repetitions for different acquisition functions. Shown is the simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials, i.e., the point which maximizes the GP posterior
mean. (Bottom) Histogram of the simple regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
\label{fig:empirical_comparison_mm}
\end{figure*}

We present results for an identical setup as reported in Section 5.1, with the
only difference being that the test functions have been sampled from a GP with
rational quadratic kernel with length scale $l=0.1$ and scale mixture
$\alpha=1.0$. The kernel used in the GP surrogate model is not modified, i.e.,
an RBF kernel with length scale $l=0.1$ is used. Thus, since different kind of
kernel govern test functions and surrogate model, we have model mismatch as
would be the common case on real-world problems. Figure
\ref{fig:empirical_comparison_mm} summarizes the results of the experiment.
Interestingly, in contrast to the experiment without model mismatch, for this setup
there are also considerable differences in the mean simple regret between MRS
and ES: while ES performs slightly better initially, it is outperformed by MRS
for $N > 60$. We suspect that this is because ES tends to explore more locally
than MRS once $p^\star$ has mostly settled onto one region of the search
space. More local exploration, however, can be detrimental in the case of
model-mismatch since the surrogate model is more likely to underestimate the
function value in regions which have not been sampled. Thus a more homogeneous
sampling of the search space as done by the more global exploration of MRS is
beneficial. As a second observation, in contrast to a no-model-mismatch
scenario, MRS$^\text{point}$ performs considerably worse than MRS when there
is model-mismatch. This emphasizes the importance of accounting for
uncertainty, particularly when there is model mis-specification.

According to the median simple regret, the difference between MRS,
MRS$^\text{point}$, ES, and EI is less pronounced in Figure
\ref{fig:empirical_comparison_mm}. Moreover, the histograms of the regret
distribution exhibit less outliers (regardless of the method). We suspect that
this stems from properties of the test functions that are sampled from a GP
with rational quadratic rather than from the model-mismatch. However,
a conclusive answer on this would require further experiments.

### 2016-05-23 2016_ICML/cmrs.tex
Adding footnote referring to supplementary material (and fixing inconsistency in p^star)

@@
 \citep[ES,][]{villemonteix_informational_2008, hennig_entropy_2012,hernandez-lobato_predictive_2014}.
-Let $p_\star(x \vert \mathcal{D}_n)$ denote the
+Let $p^\star(x \vert \mathcal{D}_n)$ denote the
 posterior distribution of the unknown optimizer $\mathbf{x}^\star = \arg\max_{\mathbf{x} \in \mathcal{X}} f(\mathbf{x})$  after
 observing $\mathcal{D}_n$. The objective of ES is to select the query point that
-results in the maximal reduction in the differential entropy of $p_\star$. More
+results in the maximal reduction in the differential entropy of $p^\star$. More
 formally, the entropy search acquisition function is defined as
@@
 where $H(\mathbf{x}^\star \vert \mathcal{D}_n)$ denotes the differential entropy
-of $p_\star(x \vert \mathcal{D}_n)$ and the expectation is with respect to the
+of $p^\star(x \vert \mathcal{D}_n)$ and the expectation is with respect to the
 predictive distribution of the GP at $\mathbf{x}$, which is a normal
@@
 samples to reduce variance, the latter incurs a run time that is quartic in the
-number of representer points used in the discretization of $p_\star$. An
+number of representer points used in the discretization of $p^\star$. An
 alternative formulation is obtained by exploiting the symmetric property of the
@@
 the uncertainty in the location of the optimizer $\mathbf{x}^\star$, i.e.,
-minimizing the differential entropy of $p_\star$, is actually different (albeit
+minimizing the differential entropy of $p^\star$, is actually different (albeit
 related) to the common external objective of minimizing the \emph{simple regret} of
@@
 model-mismatch issues and unwanted bias which could be introduced by resorting
-to common hand-crafted test functions. More specifically, we choose the
+to common hand-crafted test functions\footnote{Please refer to the supplementary material for an analogous experiment with model-mismatch.}. More specifically, we choose the
 parameter space to be the 2-dimensional unit domain $\mathcal{X} = [0, 1]^2$ and generate test
@@
 
+%\newpage
+%\appendix 
+%\input{appendix.tex}
+
 \end{document}

### 2016-05-23 2016_ICML/cmrs.tex
Fixing issue reported by ICML paper checker

@@
 \usepackage{url}
-%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
 
@@
 standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max_i y_i$.
-Since PI is known to exploit quite aggressively \cite{jones_taxonomy_2001}, a more popular
+Since PI exploits quite aggressively \cite{jones_taxonomy_2001}, a more popular
 alternative is the \emph{expected improvement} \citep[EI,][]{mockus_application_1978} over the
-current best value, which can again be computed in closed form for a GP model:
-\begin{equation*}
-\begin{split}
- a_{EI}(\mathbf{x}; \mathcal{D})
-  & := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)] \\
-  &  = \sigma_n(\mathbf{x})\left(\gamma(\mathbf{x})\Phi(\gamma(\mathbf{x})) + \phi(\gamma(\mathbf{x}))\right),
-\end{split}
-\end{equation*}
+current best value $ a_{EI}(\mathbf{x}; \mathcal{D}) := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)]$, which can again be computed in closed form for a GP model as
+$a_{EI}(\mathbf{x}; \mathcal{D})
+  = \sigma_n(\mathbf{x})\left(\gamma(\mathbf{x})\Phi(\gamma(\mathbf{x})) + \phi(\gamma(\mathbf{x}))\right)$,
 where $\phi(\cdot)$ denotes the standard Gaussian density function.  A

### 2016-05-23 2016_ICML/cmrs.tex
Final version

@@
 $R_f(\mathbf{\tilde x})$. We define the expected simple regret ER of
-selecting parameter $\mathbf{x}$ under $p(f)$ as follows:
+selecting parameter $\mathbf{x}$ under $p(f)$ as:
 $$\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
@@
 
-In $N$-step BO, we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
+In $N$-step Bayesian optimization, we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
 $X^q_N=\{\mathbf{x}^q_1, \dots, \mathbf{x}^q_N\}$ for which we evaluate $y_i = f(\mathbf{x}^q_i) +

### 2016-05-23 2016_ICML/appendix.tex
Adding apendix to main paper

@@
 \section{Synthetic Single-Task Benchmark with Model Mismatch}
+\label{section:exp_model_mismatch}
 
@@
 
-We present results for an identical setup as reported in Section 5.1, with the
+We present results for an identical setup as reported in Section \ref{Section:ResultsSingleTask},
+with the
 only difference being that the test functions have been sampled from a GP with

### 2016-05-23 2016_ICML/cmrs.tex
Adding apendix to main paper

@@
 model-mismatch issues and unwanted bias which could be introduced by resorting
-to common hand-crafted test functions\footnote{Please refer to the supplementary material for an analogous experiment with model-mismatch.}. More specifically, we choose the
+to common hand-crafted test functions\footnote{Please refer to the Appendix \ref{section:exp_model_mismatch} for an analogous experiment with model-mismatch.}. More specifically, we choose the
 parameter space to be the 2-dimensional unit domain $\mathcal{X} = [0, 1]^2$ and generate test
@@
 
-%\newpage
-%\appendix 
-%\input{appendix.tex}
+\newpage
+\appendix 
+\input{appendix.tex}
 

### 2016-05-27 2016_ICML/poster/content/left_column.tex
Template for poster

%place your content here, feel free to create subcontent files

\begin{block}{\blocktitle{Abstract}}
\justifying
Contextual policy search allows adapting robotic movement primitives to
different situations. For instance, a locomotion primitive might be adapted to
different terrain inclinations or desired walking speeds. Such an adaptation
is often achievable by modifying a small number of hyperparameters.
However, learning, when performed on real robotic systems, is typically
restricted to a small number of trials. Bayesian optimization
has recently been proposed as a sample-efficient means for contextual policy search
that is well suited under these conditions.
In this work, we extend entropy search, a variant of Bayesian optimization,
such that it can be used for \emph{active} contextual policy search where the agent
selects those tasks during training in which it expects to learn the most.
\end{block}

\begin{block}{\blocktitle{Background}}
\textbf{Contextual policy search} \cite{deisenroth_survey_2013} aims at learning an upper-level policy $\pi_\omega(\theta \vert s)$, where
\begin{itemize}
 \item $s \in \mathbb{R}^{n_s}$ encodes the current context (task)
 \item $\theta \in \mathbb{R}^{n_\theta}$ is a parameter vector for a lower-level policy such as a DMP \cite{ijspeert_dynamical_2013}
 \item $\omega \in \mathbb{R}^{n_\omega}$ is the parameter vector of the upper-level policy to be learned
\end{itemize}
such that the expected return over all contexts $J_\omega = \int_s \mu(s) \int_\theta \pi_\omega(\theta \vert s) R(s, \theta) ds d\theta$ is maximized.

One class of contextual policy search methods are \textbf{gradient-free, local-search methods} such as cost-regularized kernel regression \cite{Kober2012} and contextual relative entropy search (C-REPS) \cite{kupcsik_data-efficient_2013}.

\textbf{Bayesian optimization for contextual policy search (BO-CPS)} \cite{metzen_bayesian_2015} is an alternative model-based global-search approach, which is very efficient for low-dimensional search spaces combined with an expensive cost function.
\begin{itemize}
 \item Use surrogate model (Gaussian process) to model expected return for context-parameter pairs (allows generalization over similar contexts)
 \item Acquisition function: GP upper confidence bound (GP-UCB) \cite{srinivas_gaussian_2010}, entropy search \cite{hennig_entropy_2012}
 \item Perform optimization (DIRECT + L-BFGS) of acquisition function over parameter space for fixed context (context determined by the environment or chosen randomly)
\end{itemize}

\end{block}

\begin{block}{\blocktitle{Active Contextual Entropy Search}}
\emph{Idea:} Extend entropy search such that it allows selecting \emph{actively} the context for the next trial, in which it expects to learn the most

Entropy Search (ES):
\begin{itemize}
 \item estimate probability $p_{opt}(\theta)$ that the global optimum of unknown function $f$ is at $\theta$ at finitely many points $\{\theta^c\}_{i=1}^{N_\theta}$ and approximate using Monte Carlo integration
 \item predict the change of GP when drawing a sample at the query point
$\theta^q$ and assuming $N_y$ different outcomes $\{y^{(i)}\}$ sampled from the
GP's predictive distribution at $\theta^q$
 \item select query point that minimizes the average loss (maximizes the relative entropy) $\mathcal{L}(p_{opt}[\theta^q]) = - \int p_{opt}[\theta^q](\theta) \log \frac{p_{opt}[\theta^q](\theta)}{U_I(\theta)}, \text{d}\theta$,  where $p_{opt}[\theta^q]$ denotes the probability
 distribution of the global optimum \emph{after} an assumed query at $\theta^q$.
\end{itemize}

Active Contextual Entropy Search (ACES):
\begin{itemize}
 \item Let $p_{max}(\theta \vert s)$ denote the CPD that maximum return given context $s$ is at $\theta$
 \item Loss: expected change of relative entropy in context $s$ after performing a trial in context $s^q$with parameter $\theta^q$: $\mathcal{L}^s(s^q, \theta^q) = \mathcal{L}(p_{max}[s^q,\theta^q](\theta \vert s)) - \mathcal{L}(p_{max}(\theta \vert s))$
 \item $s^q, \theta^q = \arg\min_{(s^q, \theta^q)} \mathcal{L}^{s^q}(s^q,
\theta^q)$ would not account for information gained about the
optima in contexts $s \neq s^q$
 \item Acquisition function: $\text{ACES}(s^q, \theta^q) = \sum_{i=1}^{N_s}
\mathcal{L}^{s^c_i}(s^q, \theta^q)$, trial contexts $s^c_i \sim \mathcal{U}(S)$
 \item Evaluating $\text{ACES}(s^q, \theta^q)$ is expensive but GP has intrinsic length scales; \\approximate $\text{ACES}(s^q, \theta^q) \approx \sum_{s \in \text{NN}(s^q,
\{s^c\}, N_{nn})}  \mathcal{L}^s(s^q, \theta^q)$
 \item NN returns the $N_{nn}$ nearest neighbors of  $s^q$ in $\{s^c\}$ according to a Mahalanobis distance with the (anisotropic) GP length scales on the diagonal of the covariance
 \item Small $N_{nn}$ is faster but approximates $\text{ACES}(s^q, \theta^q)$ using only local information (local in context space), we compare $N_{nn}=1$ and $N_{nn}=20$
 \item Optimization based on CMA-ES (noisy acquisition function)
\end{itemize}
\end{block}

\begin{block}{\blocktitle{Illustration}}
\vspace*{1cm}
%\includegraphics[width=.99\columnwidth]{../pics/aces.pdf}

\end{block}

### 2016-05-27 2016_ICML/poster/content/right_column.tex
Template for poster

%place your content here, feel free to create subcontent files
\begin{block}{\blocktitle{Experimental Setup}}
\begin{center}
\raisebox{0.75cm}{
\includegraphics[width=.2\columnwidth]{pics/throw}}
\hspace*{1cm}
%\includegraphics[width=.35\columnwidth]{pics/xy_scatter_color_tau}
\hspace*{1cm}
%\includegraphics[width=.35\columnwidth]{pics/xy_scatter_color_g0}
\begin{itemize}
 \item Ball-throwing in simulation of COMPI arm (\url{github.com/rock-simulation/mars})
 \item Contexts chosen from target area: $[1, 2.5]m \times [-1, 1]m$
 \item Manually initialized joint-space DMP such that a fixed target position is hit
 \item Adapt to new target by modifying meta-parameters (execution time $\tau$ and angle of first joint $g_0$); $\tau \in [0.2, 5]$ and $g_0 \in \left[-\frac{\pi}{2}, \frac{\pi}{2}\right]$
 \item $R(s, \theta) = -\vert\vert s - b_s(\theta) \vert\vert_2^2 - 0.01\sum_t v_t^2$
 \begin{itemize}
   \item $b_s(\theta)$:  position hit for parameters $\theta$; $v_t$: joint velocities at time $t$
 \end{itemize}
 \item Deterministic affine upper-level policy; trained with C-REPS \cite{kupcsik_data-efficient_2013} update on all samples
\end{itemize}
\end{center}
\end{block}

\begin{block}{\blocktitle{Results}}
\begin{center}
\begin{itemize}
 \item Comparison of different approaches for exploration
 \begin{enumerate}
  \item Active contextual entropy search ($N_{nn} = 20$ and $N_{nn} = 1$)
  \item BO-CPS + Entropy Search +  random context selection
  \item BO-CPS + GP-UCB with $\kappa=5.0$ (``pure exploration'') + random context selection
  \item Random parameter and context selection
 \end{enumerate}
 \item Entropy Search outperforms GP-UCB because UCB aggressively samples parameters at the boundaries (high uncertainty but low global information)
 \item ACES outperforms random context selection, in particular when $N_{nn} = 20$
 \item ACES\_20 tends to avoid performing trials at the boundaries of the context space
\end{itemize}

\begin{figure}
\centering
%\includegraphics[width=0.3\textwidth,clip=true,trim=200 120 250 100]{pics/compi}
%\includegraphics[width=0.58\textwidth]{../pics/learning_curve}
%\includegraphics[width=0.4\textwidth]{../pics/context_selection}
\caption{(Left) Learning curves on the simulated robot arm COMPI: the offline performance is evaluated each 10 episodes on 16 test contexts distributed on a grid over the target area. Mean and its standard error over 20 independent runs. (Right) Scatter plot showing the sampled contexts for all (blue) and a single representative run (red).}
\label{fig:experiment}
\end{figure}

\end{center}
\end{block}

\begin{block}{\blocktitle{Outlook}}
\begin{itemize}
 \item Comparison to other active task (context) selection approaches \cite{fabisch_accounting_2015}
 \item Scaling up to higher dimensions using approaches such as REMBO
\cite{wang_bayesian_2013}
 \item Evaluation on real systems and related tasks such as robotic locomotion \cite{calandra_bayesian_2014,lizotte_automatic_2007} and robot grasping \cite{kroemer_combining_2010}
 \item More information on project BesMan (Behaviors for Mobile Manipulation):
\url{http://robotik.dfki-bremen.de/en/research/projects/besman.html}
\end{itemize}
\end{block}

\begin{block}{\blocktitle{References}}

\begin{multicols}{2}
{\scriptsize
\setbeamertemplate{bibliography item}[text]
\bibliographystyle{abbrv}
\bibliography{../literature}
}
\end{multicols}

\end{block}

### 2016-05-27 2016_ICML/poster/defines/boxes.tex
Template for poster

%set boxes

\setbeamerfont{block title}{shape=\bfseries,size=\large,parent={structure,block body}}

\newcommand{\drawboxes}{
	%boxes
	\setbeamercolor*{block body}{fg=black,bg=white}
	\setbeamercolor*{block title}{fg=black,bg=white}

	\setbeamertemplate{block begin}{
	\vskip.75ex
	\begin{beamercolorbox}[rounded=true,shadow=true,leftskip=1cm,colsep*=.75ex]{block title}%
		\usebeamerfont*{block title}\insertblocktitle
	\end{beamercolorbox}%
	{\ifbeamercolorempty[bg]{block body}{}{\nointerlineskip\vskip-0.5pt}}%
	\usebeamerfont{block body}%
	\begin{beamercolorbox}[rounded=true,shadow=true,colsep*=.75ex,sep=.75ex,vmode]{block body}%
		\ifbeamercolorempty[bg]{block body}{\vskip-.25ex}{\vskip-.75ex}\vbox{}%
	}
			\setbeamertemplate{block end}{
	\end{beamercolorbox}
			\vspace*{2ex}
	}
}

### 2016-05-27 2016_ICML/poster/defines/header.tex
Template for poster

\pgfdeclareimage[height=4.8cm]{dfki-logo}{./defines/DFKI_Schrift}

\setbeamertemplate{headline}
{%
  \setbeamercolor{mycolor}{fg=black,bg=white}
   \begin{beamercolorbox}{mycolor}
    \centering{\parbox{70cm}{\centering{\huge{\textbf{\inserttitle}}}}}\\[5mm]
    \centering{\parbox{70cm}{\centering{\Large{\insertauthor\\[.5cm] University Bremen,
Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen,
Germany\hspace{2cm}}}}}

  \end{beamercolorbox}%
  \vspace{-6cm}
}

### 2016-05-27 2016_ICML/poster/slides.tex
Template for poster

\documentclass[11pt]{beamer}
%\documentclass[11pt,handout]{beamer}

\usepackage{multimedia}

%\usetheme[secheader]{Boadilla}
\usetheme{Boadilla}

%\setbeameroption{hide notes}
%\setbeameroption{show notes}
%\setbeameroption{show only notes}
%\setbeamertemplate{note page}[plain]

\usefonttheme{structuresmallcapsserif}
\setbeamerfont{frametitle}{size=\normalsize}
\setbeamertemplate{navigation symbols}{}

\AtBeginSection[]{}

\setbeamercovered{invisible}

% Customization
%\usepackage{bibentry}
%\newcommand{\footcite}[1]{$^[$\footnote{\begin{tiny}\bibentry{#1}\end{tiny}}$^]$}
\usepackage[natbib=true, bibstyle=numeric, citestyle=authoryear,
            uniquename=false, uniquelist=false,
            firstinits=true, maxcitenames=3, minbibnames=3, maxbibnames=4,
            dashed=false, url=false, doi=false, isbn=false]{biblatex}
\newrobustcmd*{\citepub}{%
  \AtNextCite{\defcounter{minnames}{4}}\fullcite}
\newcommand{\footcitefull}[1]{$^[$\footnote{\begin{tiny}\citepub{#1}\end{tiny}}$^]$}
\addbibresource{../literature.bib}

\renewcommand{\emph}[1]{\textbf{#1}}

% Author, Title, etc.
\title[BayesOpt 2015]{Active Contextual Entropy Search}
\author[Jan Hendrik Metzen]{Jan Hendrik Metzen}
\institute[]{AG Robotik, University Bremen\\ Project BesMan \url{http://robotik.dfki-bremen.de/en/research/projects/besman.html}}
\date[12/12/15]{BayesOpt 2015, December 12, 2015}

\begin{document}

\frame{\titlepage}

\begin{frame}{Overview}
   \begin{itemize}
     \item We apply Bayesian optimization to multi-task robotic behavior learning  (contextual policy search\footcitefull{deisenroth_survey_2013})
     \item We focus on problems
     \begin{itemize}
       \item which are low-dimensional
       \item where the possible number of evaluations is very small
       \item thus, in general, well-suited for Bayesian optimization\footcitefull{metzen_bayesian_2015}
     \end{itemize}
     \item We propose \emph{Active Contextual Entropy Search} (ACES)
     \begin{itemize}
       \item an extension of entropy search\footcitefull{hennig_entropy_2012}
       \item suited for contextual problems (multi-task learning)
       \item allows actively selecting contexts (active learning)
     \end{itemize}
   \end{itemize}
\end{frame}

\begin{frame}{Results}
   \begin{itemize}
     \item \emph{Scenario:} Simulated ball-throwing with a robotic arm
    \end{itemize}
    \begin{center}
       \includegraphics[width=.4\textwidth]{pics/compi.png}
       \hspace{1cm}
       \includegraphics[width=.25\textwidth]{pics/xy_scatter_color_g0}
   \end{center}

   \vspace*{-.5cm}
   \begin{center}
       \begin{minipage}[b][5cm][c]{.59\textwidth}
        \begin{itemize}
            \item To be learned: generalization of throw behavior to different target positions (contexts)
            \item Movement primitive fixed, only meta-parameters adapted
            \item ACES allows actively selecting target positions to be practiced
            \item ACES outperforms passive task selection
        \end{itemize}
        \end{minipage}
       \includegraphics[width=.4\textwidth]{../pics/learning_curve}
   \end{center}
   \vspace*{-.5cm}
   \begin{center}
   More details on the poster. Hope to see you there!
   \end{center}
\end{frame}
\end{document}

### 2016-05-27 2016_ICML/poster/content/left_column.tex
Updating title/abstract and some pics

@@
 \justifying
-Contextual policy search allows adapting robotic movement primitives to
-different situations. For instance, a locomotion primitive might be adapted to
-different terrain inclinations or desired walking speeds. Such an adaptation
-is often achievable by modifying a small number of hyperparameters.
-However, learning, when performed on real robotic systems, is typically
-restricted to a small number of trials. Bayesian optimization
-has recently been proposed as a sample-efficient means for contextual policy search
-that is well suited under these conditions.
-In this work, we extend entropy search, a variant of Bayesian optimization,
-such that it can be used for \emph{active} contextual policy search where the agent
-selects those tasks during training in which it expects to learn the most.
+We propose minimum regret search (MRS), a novel acquisition function for Bayesian
+optimization. MRS bears similarities with information-theoretic approaches
+such as entropy search (ES). However, while ES aims in each query at maximizing the
+information gain with respect to the global maximum, MRS aims at minimizing the
+expected simple regret of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
+cases, MRS produces fewer outliers with high simple regret than ES. We provide empirical
+results both for a synthetic single-task optimization problem as well as for a
+simulated multi-task robotic control problem.
 \end{block}
@@
 \vspace*{1cm}
-%\includegraphics[width=.99\columnwidth]{../pics/aces.pdf}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.4\columnwidth]{../pics/regret_illustration}
+\includegraphics[width=0.4\columnwidth]{../pics/acq_comparison}
+\caption{(Left) Illustration of GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on the right-hand side).
+(Right) Illustration of GP posterior and different acquisition function.
+Absolute values have been normalized such that the mean value of an acquisition function is $0.5$.
+Best seen in color.}
+\label{fig:MRS_illustration}
+\end{figure}
 

### 2016-05-27 2016_ICML/poster/content/right_column.tex
Updating title/abstract and some pics

@@
 \centering
-%\includegraphics[width=0.3\textwidth,clip=true,trim=200 120 250 100]{pics/compi}
-%\includegraphics[width=0.58\textwidth]{../pics/learning_curve}
-%\includegraphics[width=0.4\textwidth]{../pics/context_selection}
-\caption{(Left) Learning curves on the simulated robot arm COMPI: the offline performance is evaluated each 10 episodes on 16 test contexts distributed on a grid over the target area.
-Mean and its standard error over 20 independent runs.
-(Right) Scatter plot showing the sampled contexts for all (blue) and a single representative run (red).}
-\label{fig:experiment}
+\includegraphics[width=.9\columnwidth]{../pics/empirical_comparison} \\
+\includegraphics[width=.9\columnwidth]{../pics/hist}
+\caption{(Top) Median and mean simple regret over $250$ repetitions for different acquisition functions.
+Shown is the simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials, i.e., the point which maximizes the GP posterior
+mean. (Bottom) Histogram of the simple regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
+\label{fig:empirical_comparison}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{../pics/es_analysis}
+\caption{Illustration of acquisition functions on a target function for
+100 given samples and 25 representer points; darker areas correspond to larger values.
+ES focuses on sampling in areas with high density of $p^\star$ (many representer points), while MRS focuses on unexplored areas that are populated by representer points (non-zero $p^\star$).
+}
+\label{fig:es_analysis}
 \end{figure}

### 2016-05-27 2016_ICML/poster/defines/header.tex
Updating title/abstract and some pics

@@
     \centering{\parbox{70cm}{\centering{\Large{\insertauthor\\[.5cm] University Bremen,
-Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen,
-Germany\hspace{2cm}}}}}
+Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen, Germany\\
+Corporate Research CR/AEY2, Robert Bosch GmbH, 70442 Stuttgart, Germany
+}}}}
 

### 2016-05-31 2016_ICML/poster/defines/header.tex
Working on poster layout

--- 2016-05-27 2016_ICML/poster/defines/header.tex
@@
-\pgfdeclareimage[height=4.8cm]{dfki-logo}{./defines/DFKI_Schrift}
+\pgfdeclareimage[height=2.8cm]{dfki-logo}{./defines/Bosch-Logo}
 
@@
     \centering{\parbox{70cm}{\centering{\Large{\insertauthor\\[.5cm] University Bremen,
-Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen,
-Germany\hspace{2cm}}}}}
+Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen, Germany\\
+Robert Bosch GmbH, Corporate Research CR/AEY2, 70442 Stuttgart, Germany
+}}}}
 

### 2016-05-31 2016_ICML/poster/content/left_column.tex
Poster content

@@
 \begin{block}{\blocktitle{Background}}
-\textbf{Contextual policy search} \cite{deisenroth_survey_2013} aims at learning an upper-level policy $\pi_\omega(\theta \vert s)$, where
+\textbf{Bayesian optimization} \cite{shahriari_taking_2016}:
 \begin{itemize}
- \item $s \in \mathbb{R}^{n_s}$ encodes the current context (task)
- \item $\theta \in \mathbb{R}^{n_\theta}$ is a parameter vector for a lower-level policy such as a DMP \cite{ijspeert_dynamical_2013}
- \item $\omega \in \mathbb{R}^{n_\omega}$ is the parameter vector of the upper-level policy to be learned
+\item aims at black-box optimization problems $\mathbf{x} = \arg\min_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
+\item maintains a \emph{probabilistic model} for $f(\mathbf{x})$, typically a Gaussian process (GP)
+\item decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next based on GP posterior of first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}
 \end{itemize}
-such that the expected return over all contexts $J_\omega = \int_s \mu(s) \int_\theta \pi_\omega(\theta \vert s) R(s, \theta) ds d\theta$ is maximized.
 
-One class of contextual policy search methods are \textbf{gradient-free, local-search methods} such as cost-regularized kernel regression \cite{Kober2012} and contextual relative entropy search (C-REPS) \cite{kupcsik_data-efficient_2013}.
-
-\textbf{Bayesian optimization for contextual policy search (BO-CPS)} \cite{metzen_bayesian_2015} is an alternative model-based global-search approach, which is very efficient for low-dimensional search spaces combined with an expensive cost function.
+Acquisition functions decide where to query next:
 \begin{itemize}
- \item Use surrogate model (Gaussian process) to model expected return for context-parameter pairs (allows generalization over similar contexts)
- \item Acquisition function: GP upper confidence bound (GP-UCB) \cite{srinivas_gaussian_2010}, entropy search \cite{hennig_entropy_2012}
- \item Perform optimization (DIRECT + L-BFGS) of acquisition function over parameter space for fixed context (context determined by the environment or chosen randomly)
+\item Upper-Confidence Bound (UCB): $a_{UCB}(\mathbf{x};
+\mathcal{D}_n) = \mu_{n}(\mathbf{x}) + \kappa_n \sigma_{n}(\mathbf{x})$
 \end{itemize}
@@
 
-\begin{block}{\blocktitle{Active Contextual Entropy Search}}
-\emph{Idea:} Extend entropy search such that it allows selecting \emph{actively} the context for the next trial, in which it expects to learn the most
+\begin{block}{\blocktitle{Minimum Regret Search}}
+\emph{Idea:}
 
@@
 
-Active Contextual Entropy Search (ACES):
+Minimum Regret Search (MRS):
 \begin{itemize}
- \item Let $p_{max}(\theta \vert s)$ denote the CPD that maximum return given context $s$ is at $\theta$
- \item Loss: expected change of relative entropy in context $s$ after performing a trial in context $s^q$with parameter $\theta^q$: $\mathcal{L}^s(s^q, \theta^q) = \mathcal{L}(p_{max}[s^q,\theta^q](\theta \vert s)) - \mathcal{L}(p_{max}(\theta \vert s))$
- \item $s^q, \theta^q = \arg\min_{(s^q, \theta^q)} \mathcal{L}^{s^q}(s^q,
-\theta^q)$ would not account for information gained about the
-optima in contexts $s \neq s^q$
- \item Acquisition function: $\text{ACES}(s^q, \theta^q) = \sum_{i=1}^{N_s}
-\mathcal{L}^{s^c_i}(s^q, \theta^q)$, trial contexts $s^c_i \sim \mathcal{U}(S)$
- \item Evaluating $\text{ACES}(s^q, \theta^q)$ is expensive but GP has intrinsic length scales; \\approximate $\text{ACES}(s^q, \theta^q) \approx \sum_{s \in \text{NN}(s^q,
-\{s^c\}, N_{nn})}  \mathcal{L}^s(s^q, \theta^q)$
- \item NN returns the $N_{nn}$ nearest neighbors of  $s^q$ in $\{s^c\}$ according to a Mahalanobis distance with the (anisotropic) GP length scales on the diagonal of the covariance
- \item Small $N_{nn}$ is faster but approximates $\text{ACES}(s^q, \theta^q)$ using only local information (local in context space), we compare $N_{nn}=1$ and $N_{nn}=20$
- \item Optimization based on CMA-ES (noisy acquisition function)
+ \item 
 \end{itemize}
@@
 \centering
-\includegraphics[width=0.4\columnwidth]{../pics/regret_illustration}
-\includegraphics[width=0.4\columnwidth]{../pics/acq_comparison}
+\includegraphics[width=0.48\columnwidth]{../pics/regret_illustration}
+\includegraphics[width=0.48\columnwidth]{../pics/acq_comparison}
 \caption{(Left) Illustration of GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on the right-hand side).
@@
 \end{figure}
+\end{block}
+
+\begin{block}{\blocktitle{Synthetic Single-Task Benchmark}}
+\begin{itemize}
+ \item Comparison of different approaches for exploration
+ \begin{enumerate}
+  \item Active contextual entropy search ($N_{nn} = 20$ and $N_{nn} = 1$)
+  \item BO-CPS + Entropy Search +  random context selection
+  \item BO-CPS + GP-UCB with $\kappa=5.0$ (``pure exploration'') + random context selection
+  \item Random parameter and context selection
+ \end{enumerate}
+ \item Entropy Search outperforms GP-UCB because UCB aggressively samples parameters at the boundaries (high uncertainty but low global information)
+ \item ACES outperforms random context selection, in particular when $N_{nn} = 20$
+ \item ACES\_20 tends to avoid performing trials at the boundaries of the context space
+\end{itemize}
 

### 2016-05-31 2016_ICML/poster/content/right_column.tex
Poster content

@@
 %place your content here, feel free to create subcontent files
-\begin{block}{\blocktitle{Experimental Setup}}
-\begin{center}
-\raisebox{0.75cm}{
-\includegraphics[width=.2\columnwidth]{pics/throw}}
-\hspace*{1cm}
-%\includegraphics[width=.35\columnwidth]{pics/xy_scatter_color_tau}
-\hspace*{1cm}
-%\includegraphics[width=.35\columnwidth]{pics/xy_scatter_color_g0}
-\begin{itemize}
- \item Ball-throwing in simulation of COMPI arm (\url{github.com/rock-simulation/mars})
- \item Contexts chosen from target area: $[1, 2.5]m \times [-1, 1]m$
- \item Manually initialized joint-space DMP such that a fixed target position is hit
- \item Adapt to new target by modifying meta-parameters (execution time $\tau$ and angle of first joint $g_0$); $\tau \in [0.2, 5]$ and $g_0 \in \left[-\frac{\pi}{2}, \frac{\pi}{2}\right]$
- \item $R(s, \theta) = -\vert\vert s - b_s(\theta) \vert\vert_2^2 - 0.01\sum_t v_t^2$
- \begin{itemize}
-   \item $b_s(\theta)$:  position hit for parameters $\theta$; $v_t$: joint velocities at time $t$
- \end{itemize}
- \item Deterministic affine upper-level policy; trained with C-REPS \cite{kupcsik_data-efficient_2013} update on all samples
-\end{itemize}
-\end{center}
-\end{block}
 
@@
 \begin{center}
-\begin{itemize}
- \item Comparison of different approaches for exploration
- \begin{enumerate}
-  \item Active contextual entropy search ($N_{nn} = 20$ and $N_{nn} = 1$)
-  \item BO-CPS + Entropy Search +  random context selection
-  \item BO-CPS + GP-UCB with $\kappa=5.0$ (``pure exploration'') + random context selection
-  \item Random parameter and context selection
- \end{enumerate}
- \item Entropy Search outperforms GP-UCB because UCB aggressively samples parameters at the boundaries (high uncertainty but low global information)
- \item ACES outperforms random context selection, in particular when $N_{nn} = 20$
- \item ACES\_20 tends to avoid performing trials at the boundaries of the context space
-\end{itemize}
 
@@
 \centering
-\includegraphics[width=.9\columnwidth]{../pics/empirical_comparison} \\
-\includegraphics[width=.9\columnwidth]{../pics/hist}
-\caption{(Top) Median and mean simple regret over $250$ repetitions for different acquisition functions.
-Shown is the simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials, i.e., the point which maximizes the GP posterior
-mean. (Bottom) Histogram of the simple regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
+\includegraphics[width=.8\columnwidth]{../pics/empirical_comparison} \\
+\includegraphics[width=.8\columnwidth]{../pics/hist}
+\caption{\emph{No model mismatch:} Simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials over $250$ repetitions for different acquisition functions.}
 \label{fig:empirical_comparison}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=.8\textwidth]{../pics/empirical_comparison_mm} \\
+\includegraphics[width=.8\textwidth]{../pics/hist_mm}
+\caption{\emph{Model mismatch:} Simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials over $250$ repetitions for different acquisition functions.}
+\label{fig:empirical_comparison_mm}
+\end{figure}
+
 \end{center}
@@
 \begin{itemize}
- \item Comparison to other active task (context) selection approaches \cite{fabisch_accounting_2015}
- \item Scaling up to higher dimensions using approaches such as REMBO
-\cite{wang_bayesian_2013}
- \item Evaluation on real systems and related tasks such as robotic locomotion \cite{calandra_bayesian_2014,lizotte_automatic_2007} and robot grasping \cite{kroemer_combining_2010}
- \item More information on project BesMan (Behaviors for Mobile Manipulation):
-\url{http://robotik.dfki-bremen.de/en/research/projects/besman.html}
+ \item For multi-task learning and results on simulated robotic task: see paper
+ \item Open questions: treatment of GP hyperparameters, more efficient approximation techniques for MRS, regret bounds for MRS?
 \end{itemize}

### 2016-06-01 2016_ICML/poster/content/left_column.tex
Further work on poster

@@
 \begin{itemize}
-\item aims at black-box optimization problems $\mathbf{x} = \arg\min_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
-\item maintains a \emph{probabilistic model} for $f(\mathbf{x})$, typically a Gaussian process (GP)
+\item black-box optimization problems $\mathbf{x} = \arg\min_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
+\item maintains a \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
 \item decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next based on GP posterior of first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}
+\item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
+\item objective: minimize \emph{simple regret} 
+$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$
 \end{itemize}
@@
 \mathcal{D}_n) = \mu_{n}(\mathbf{x}) + \kappa_n \sigma_{n}(\mathbf{x})$
+\item Probability of Improvement (PI): $a_{PI}(\mathbf{x}; \mathcal{D}_n) := \mathbb{P}[f(\mathbf{x}) > \tau]$
+\item Expected Improvement (EI): $a_{EI}(\mathbf{x}; \mathcal{D}_n) := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)]$
+\item Entropy Search (ES) \cite{hennig_entropy_2012}: $a_{ES}(\mathbf{x}, \mathcal{D}_n)
+  = H(\mathbf{x}^\star \vert \mathcal{D}_n) - \mathbb{E}_{y \vert \mathbf{x}, \mathcal{D}_n}
+	[H(\mathbf{x}^\star \vert \mathcal{D}_n \cup \{(\mathbf{x}, y))]$,
+	where $H(\mathbf{x}^\star \vert \mathcal{D}_n)$ denotes the differential entropy
+of the posterior distribution $p^\star(x \vert \mathcal{D}_n)$ of the unknown optimizer $\mathbf{x}^\star = \arg\max_{\mathbf{x} \in \mathcal{X}} f(\mathbf{x})$.
 \end{itemize}
@@
 \begin{block}{\blocktitle{Minimum Regret Search}}
-\emph{Idea:}
 
-Entropy Search (ES):
 \begin{itemize}
@@
 
-Minimum Regret Search (MRS):
+Approximation:
 \begin{itemize}
  \item 
+ \item $n_f=1000$, $n_r=25$, and $n_y=51$
 \end{itemize}
@@
 \includegraphics[width=0.48\columnwidth]{../pics/acq_comparison}
-\caption{(Left) Illustration of GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on the right-hand side).
-(Right) Illustration of GP posterior and different acquisition function.
-Absolute values have been normalized such that the mean value of an acquisition function is $0.5$.
-Best seen in color.}
+\caption{(Left) GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on right-hand side).
+(Right) GP posterior and different acquisition function.
+Absolute values have been normalized such that the mean value of acquisition function is $0.5$.}
 \label{fig:MRS_illustration}
@@
 \end{block}
-
-\begin{block}{\blocktitle{Synthetic Single-Task Benchmark}}
-\begin{itemize}
- \item Comparison of different approaches for exploration
- \begin{enumerate}
-  \item Active contextual entropy search ($N_{nn} = 20$ and $N_{nn} = 1$)
-  \item BO-CPS + Entropy Search +  random context selection
-  \item BO-CPS + GP-UCB with $\kappa=5.0$ (``pure exploration'') + random context selection
-  \item Random parameter and context selection
- \end{enumerate}
- \item Entropy Search outperforms GP-UCB because UCB aggressively samples parameters at the boundaries (high uncertainty but low global information)
- \item ACES outperforms random context selection, in particular when $N_{nn} = 20$
- \item ACES\_20 tends to avoid performing trials at the boundaries of the context space
-\end{itemize}
-
-\end{block}

### 2016-06-01 2016_ICML/poster/content/right_column.tex
Further work on poster

@@
 
-\begin{block}{\blocktitle{Results}}
+\begin{block}{\blocktitle{Synthetic Single-Task Benchmark}}
+\begin{itemize}
+ \item Target functions sampled from a generative model (GP with isotropic RBF kernel
+of length scale $l = 0.1$ and unit signal variance) on $\mathcal{X} = [0, 1]^2$ 
+ \item In practice: sample $250$ function values from GP, fit GP to these function values and use resulting posterior mean as target function
+ \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
+ \item Model mismatch: target functions from GP with rational quadratic kernel but RBF kernel in surrogate model
+\end{itemize}
+
 \begin{center}
@@
 \includegraphics[width=.8\columnwidth]{../pics/hist}
-\caption{\emph{No model mismatch:} Simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials over $250$ repetitions for different acquisition functions.}
+\caption{Simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials over $250$ repetitions for different acquisition functions (\emph{no model mismatch})}
 \label{fig:empirical_comparison}
@@
 \centering
-\includegraphics[width=.9\textwidth]{../pics/es_analysis}
-\caption{Illustration of acquisition functions on a target function for
-100 given samples and 25 representer points; darker areas correspond to larger values.
+\includegraphics[width=.8\textwidth]{../pics/es_analysis}
+\caption{Acquisition functions on a target function at $N=100$ and 25 representer points; darker areas correspond to larger values.
 ES focuses on sampling in areas with high density of $p^\star$ (many representer points), while MRS focuses on unexplored areas that are populated by representer points (non-zero $p^\star$).
@@
 \includegraphics[width=.8\textwidth]{../pics/hist_mm}
-\caption{\emph{Model mismatch:} Simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials over $250$ repetitions for different acquisition functions.}
+\caption{Result for setting with \emph{model mismatch}}
 \label{fig:empirical_comparison_mm}
@@
 \begin{itemize}
- \item For multi-task learning and results on simulated robotic task: see paper
+ \item For multi-task MRS and results on simulated robotic task: see paper
  \item Open questions: treatment of GP hyperparameters, more efficient approximation techniques for MRS, regret bounds for MRS?
+ \item Source code: \url{https://github.com/jmetzen/bayesian_optimization}
 \end{itemize}
@@
 \begin{block}{\blocktitle{References}}
-
+\vspace*{-.75cm}
 \begin{multicols}{2}

### 2016-06-01 2016_ICML/poster/content/left_column.tex
Poster (MRS section)

@@
 cases, MRS produces fewer outliers with high simple regret than ES. We provide empirical
-results both for a synthetic single-task optimization problem as well as for a
-simulated multi-task robotic control problem.
+results for a synthetic single-task optimization problem.
 \end{block}
@@
 
+Minimum regret search (MRS): acquistion function based directly on external objective of minimizing simple regret
 \begin{itemize}
- \item estimate probability $p_{opt}(\theta)$ that the global optimum of unknown function $f$ is at $\theta$ at finitely many points $\{\theta^c\}_{i=1}^{N_\theta}$ and approximate using Monte Carlo integration
- \item predict the change of GP when drawing a sample at the query point
-$\theta^q$ and assuming $N_y$ different outcomes $\{y^{(i)}\}$ sampled from the
-GP's predictive distribution at $\theta^q$
- \item select query point that minimizes the average loss (maximizes the relative entropy) $\mathcal{L}(p_{opt}[\theta^q]) = - \int p_{opt}[\theta^q](\theta) \log \frac{p_{opt}[\theta^q](\theta)}{U_I(\theta)}, \text{d}\theta$,  where $p_{opt}[\theta^q]$ denotes the probability
- distribution of the global optimum \emph{after} an assumed query at $\theta^q$.
+ \item Expected simple regret: $\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
+= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
+x})]$
+ \item For fixed GP $p(f)$, $\arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
+ \item MRS aims at selecting query points s.t. ER is minimized also with respect to resulting $p(f)$
+ \item Myopic choice: select next query point s.t. minimum ER is reduced the most (in expectation)
+ \item $a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
+	= \min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x})
+	 - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]$
+ \item Additionally also account for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ yields MRS
+ \item $a_{\text{MRS}}(\mathbf{x}^q)
+    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}[\text{ER}(p_n)(\mathbf{\tilde x})] 
+	   - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[
+		  \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n \cup \{(\mathbf{x}^q, y)\}}}[
+			 \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]]$
 \end{itemize}
 
-Approximation:
+Approximate $a_{\text{MRS}}$ based on sampling:
 \begin{itemize}
- \item 
- \item $n_f=1000$, $n_r=25$, and $n_y=51$
+ \item approximate $\mathbb{E}_{p(f)}$ by taking $n_f=1000$ Monte Carlo samples from $p(f)$
+ \item approximate $\mathbb{E}_{y \vert p(f), \mathbf{x}^q}$  by taking
+$n_y=51$ Monte Carlo samples from $p(f)$'s predictive distribution at
+$\mathbf{x}_q$
+ \item discretize $p^\star$ to a finite set of $n_r=25$ representer points (Thompson
+sampling from $p(f)$ on candidate points)
+ \item estimating $p^\star_{\mathcal{D}_n}$ on representer points by reusing the samples used 
+for approximating $\mathbb{E}_{p(f)}$
+\item Common random numbers in estimation of
+$\text{ER}(p)(\mathbf{x})$ for different $p(f)$ reduces variance
 \end{itemize}

### 2016-06-05 2016_ICML/presentation/main.tex
Adding presentation template

\documentclass[11pt]{beamer}
%\documentclass[11pt,handout]{beamer}

\usepackage{multimedia}

%\usetheme[secheader]{Boadilla}
\usetheme{Boadilla}

%\setbeameroption{hide notes}
%\setbeameroption{show notes}
%\setbeameroption{show only notes}
%\setbeamertemplate{note page}[plain]

\usefonttheme{structuresmallcapsserif}
\setbeamerfont{frametitle}{size=\normalsize}
\setbeamertemplate{navigation symbols}{}

\AtBeginSection[]{}

\setbeamercovered{invisible}

% Custom packages
\usepackage{bibentry}
\usepackage{color}

\usepackage{animate}

% Customization
\newcommand{\footcite}[1]{$^[$\footnote{\begin{tiny}\bibentry{#1}\end{tiny}}$^]$}

\renewcommand{\emph}[1]{\textbf{#1}}

\newcommand{\taskparam}{{\color{red} \tau}}
\newcommand{\skillparam}{{\color{blue} \theta}}

\newcommand{\newblock}{}

% Author, Title, etc.
\title[EWRL 2013]{Learning Skill Templates for Parameterized Tasks}
\author[Metzen \& Fabisch]{Jan Hendrik Metzen and Alexander Fabisch}
\institute[University Bremen]{AG Robotik, University Bremen\\ Project BesMan \url{http://robotik.dfki-bremen.de/de/forschung/projekte/besman.html}}
\date[05-09/08/13]{EWRL, August 05-09, 2013}

\begin{document}

\frame{\titlepage
       \bibliographystyle{abbrv}
       \nobibliography{../references}}

\begin{frame}{Motivation: Learn Skills for Robotic Mobile Manipulation}
   \begin{center}
   \movie[width=8cm,height=6cm,externalviewer]
             {\includegraphics[width=8cm,height=6cm]{PA10_Throwing_Ball}}{targets_short.avi} \\
   Example: learn to throw a ball at different targets
   \end{center}
\end{frame}

\begin{frame}{Multi-Task Reinforcement Learning}
  Given:
  \begin{itemize}
    \item Class of RL problems parameterized by $\taskparam \in T \subseteq \mathbb{R}^n$
    \item Task distribution $P(\taskparam)$ {\tiny [in this talk uniform over $T$]}
    \item Skill represented by a parameterized policy with parameter vector $\skillparam \in
\mathbb{R}^m$
    \item Means for determining return $J(\skillparam, \taskparam)$ of the skill parametrized by $\skillparam$ in task $\taskparam$
  \end{itemize}
  \pause
  Parameterized skill \footcite{da_silva_learning_2012}:
  \begin{itemize}
    \item Learn a function $\hat{\Theta}: \taskparam \mapsto \skillparam_\taskparam$ from task vector $\taskparam$ to a skill vector $\skillparam_\taskparam$
    \item Objective: $\hat{\Theta}$ similar to $\Theta^* = \arg\max_\Theta \int P(\taskparam)J(\Theta(\taskparam),\taskparam)d\taskparam$
    \item Typically: $\hat{\Theta}(\taskparam) \neq \arg\max_\skillparam J(\skillparam,\taskparam)$
  \end{itemize}
  \pause
  Our approach: give more than point estimate $\hat{\Theta}(\taskparam)$
\end{frame}

\begin{frame}{Learning Skill Templates}
  Given:
  \begin{itemize}
    \item Training set from $K$ source tasks $E = \left\{(\taskparam_i, \skillparam_{\taskparam_i}) \vert i=1,\dots,K\right\}$ with $J(\skillparam_{\taskparam_i},\taskparam_i) \approx J(\skillparam_{\taskparam_i}^*,\taskparam_i)$
    \item $E$ can be generated using RL (e.g., direct policy search) in each of the tasks
  \end{itemize}
 \pause
 Skill Templates
 \begin{itemize}
    \item \emph{Goal}: Transfer procedural knowledge contained in $E$ to novel, $(K+1)$st tasks $\tau$
    \item \emph{Idea}: learn to initialize policy search for new task such that close-to-optimal policies can be learned more sample-efficiently
    \item Skill template: $\psi: \taskparam \mapsto \mathcal{N}(\Theta(\taskparam), \Omega(\taskparam))$
    \item Normal distribution over policy parameter space, where
    \begin{itemize}
      \item $\Theta(\taskparam) \in \mathbb{R}^m$ determines starting point for policy search
      \item $\Omega(\taskparam) \in \mathbb{R}^{m\times m}$ controls initial exploration
    \end{itemize}
    \item Skill template learned from $E$
  \end{itemize}

\end{frame}

\begin{frame}{Approach}
  \begin{itemize}
    \item Represent skills using dynamical systems movement primitives (DMPs)\footcite{Ijspeert2013}\footcite{mulling_learning_2012}
    \item Learn source task policies using policy search based on CMA-ES \footcite{hansen_completely_2001}
    \item Learn $\Theta: \taskparam \mapsto \skillparam_\taskparam$ from E using Gaussian Process Regression (GPR) \footcite{rasmussen_gaussian_2006}
    \item Restrict $\Omega$ to the diagonal case {\tiny [for now]}:
    \begin{enumerate}
      \item Weight-proportional exploration: $\Omega(\taskparam)_{ii}$ proportional to $\vert\Theta(\taskparam)_i\vert$
      \item Uncertainty exploration: $\Omega(\taskparam)_{ii}$ proportional to uncertainty in GPR's prediction of $\Theta_i$
    \end{enumerate}
    \item Normalize mean eigenvalue of $\Omega(\taskparam)$
  \end{itemize}
\end{frame}

\begin{frame}{Test domain}
  \begin{itemize}
    \item Learn to throw a ball with a simulated PA-$10$
    \item $\taskparam \in \mathbb{R}^2$: target position on floor
    \item $\skillparam \in \mathbb{R}^{96}$: DMP parameters controlling robot in joint space ($8$ joints):
    \begin{itemize}
      \item Joint's trajectory ($10$ parameters per joint)
      \item Joint's final position and velocity ($2$ parameters per joint)
    \end{itemize}
    \item $J(\skillparam,\taskparam)$: Negative of squared distance of thrown ball from target
  \end{itemize}
  \begin{center}
    \includegraphics[width=.6\linewidth]{PA10_Throwing_Ball}
  \end{center}
\end{frame}

\begin{frame}{Illustration: Ball Throwing (1/2)}
   \begin{center}
   Error of $\Theta(\taskparam)$ vs.\,Number of Source Tasks
   \end{center}
   \begin{center}
         \only<1>{\includegraphics[width=\linewidth]
                   {plots/prediction_error_00}}
         \only<2>{\includegraphics[width=\linewidth]
                   {plots/prediction_error_01}}
         \only<3>{\includegraphics[width=\linewidth]
                   {plots/prediction_error_03}}
         \only<4>{\includegraphics[width=\linewidth]
                   {plots/prediction_error_05}}
         \only<5>{\includegraphics[width=\linewidth]
                   {plots/prediction_error_09}}
   \end{center}
\end{frame}

\begin{frame}{Illustration: Ball Throwing (2/2)}
   \begin{center}
   Error during Learning (Tabula Rasa vs.\,Skill Template (Uncertainty))
   \end{center}
   \begin{center}
         \only<1>{\includegraphics[width=\linewidth]
                   {plots/error_during_learning_00}}
         \only<2>{\includegraphics[width=\linewidth]
                   {plots/error_during_learning_01}}
         \only<3>{\includegraphics[width=\linewidth]
                   {plots/error_during_learning_02}}
         \only<4>{\includegraphics[width=\linewidth]
                   {plots/error_during_learning_03}}
         \only<5>{\includegraphics[width=\linewidth]
                   {plots/error_during_learning_04}}
         \only<6>{\includegraphics[width=\linewidth]
                   {plots/error_during_learning_05}}
   \end{center}
\end{frame}

\begin{frame}{Results: Ball Throwing}
   \begin{center}
   Learning Curve (Tabula Rasa vs.\,ST with different $\Omega$)
   \end{center}
   \begin{center}
         \includegraphics[width=.8\linewidth]{plots/learning_curve}\\
         Initial exploration covariance matrix matters (even with CMA-ES)
   \end{center}
\end{frame}

\begin{frame}{Outlook and Discussion}
  Open questions and future work:
  \begin{itemize}
    \item Correlated skill parameter dimensions: how to learn non-diagonal $\Omega \in \mathbb{R}^{m \times m}$ from small set of source tasks?
    \item Off-task learning: how to learn from $\skillparam_{\taskparam}$ with $J(\skillparam_{\taskparam},\taskparam) \ll J(\skillparam_{\taskparam}^*,\taskparam)$?
    \item Best way to handle discontinuities in mapping $\Theta$ (like fore- vs.\,backhand)?
    \item Learn $\Theta$ using (non-parametric) regression or (parametric) policy search?
    \pause
    \item Evaluation on humanoid robot AILA (simulated and real)
  \end{itemize}

  \begin{center}
    \includegraphics[width=.39\linewidth]{AILA}
  \end{center}
  \pause
  \begin{center}
   Thank you for your attention!
   Do you have questions, comments, or ideas?
   \end{center}

\end{frame}

\end{document}

### 2016-06-07 2016_ICML/poster/content/left_column.tex
Adding further illustrating examples

@@
 \centering
-\includegraphics[width=0.48\columnwidth]{../pics/regret_illustration}
+\includegraphics[width=0.48\columnwidth]{../pics/regret_illustration_2}
+\includegraphics[width=0.48\columnwidth]{../pics/regret_scatter}
+\caption{(Left) GP posterior, probability of maximum $p^\star$, and expected regret ER.
+(Right) Scatter plot of position of optimum and regret of $\mathbf{\tilde x} = 1.5$ versus optimum in sample functions.}
+\label{fig:MRS_illustration}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics[width=0.48\columnwidth]{../pics/acq_comparison}
-\caption{(Left) GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on right-hand side).
-(Right) GP posterior and different acquisition function.
-Absolute values have been normalized such that the mean value of acquisition function is $0.5$.}
+\caption{GP posterior and different acquisition function. Absolute values have been normalized such that the mean value of acquisition function is $0.5$.}
 \label{fig:MRS_illustration}

### 2016-06-07 2016_ICML/presentation/main.tex
Working on presentation

@@
 
-\newcommand{\newblock}{}
+%\newcommand{\newblock}{}
 
 % Author, Title, etc.
-\title[EWRL 2013]{Learning Skill Templates for Parameterized Tasks}
-\author[Metzen \& Fabisch]{Jan Hendrik Metzen and Alexander Fabisch}
-\institute[University Bremen]{AG Robotik, University Bremen\\ Project BesMan \url{http://robotik.dfki-bremen.de/de/forschung/projekte/besman.html}}
-\date[05-09/08/13]{EWRL, August 05-09, 2013}
+\title[ICML 2016]{Minimum Regret Search for Single- and Multi-Task Optimization}
+\author[Jan Hendrik Metzen]{Jan Hendrik Metzen}
+\institute[]{University Bremen, Robotics Research Group \\ Robert Bosch GmbH, Corporate Research CR/AEY2}
+\date[06/19/16]{ICML, June 19, 2016}
 
@@
        \bibliographystyle{abbrv}
-       \nobibliography{../references}}
+       \nobibliography{../literature}}
 
-\begin{frame}{Motivation: Learn Skills for Robotic Mobile Manipulation}
-   \begin{center}
-   \movie[width=8cm,height=6cm,externalviewer]
-             {\includegraphics[width=8cm,height=6cm]{PA10_Throwing_Ball}}{targets_short.avi} \\
-   Example: learn to throw a ball at different targets
-   \end{center}
+\begin{frame}{Motivation: Bayesian optimization}
+
 \end{frame}
 
-\begin{frame}{Multi-Task Reinforcement Learning}
-  Given:
+\begin{frame}{Bayesian Optimization}
+\textbf{Bayesian optimization}\footcite{shahriari_taking_2016}:
 \begin{itemize}
-    \item Class of RL problems parameterized by $\taskparam \in T \subseteq \mathbb{R}^n$
-    \item Task distribution $P(\taskparam)$ {\tiny [in this talk uniform over $T$]}
-    \item Skill represented by a parameterized policy with parameter vector $\skillparam \in
-\mathbb{R}^m$
-    \item Means for determining return $J(\skillparam, \taskparam)$ of the skill parametrized by $\skillparam$ in task $\taskparam$
+\item black-box optimization problems: $\mathbf{x} = \arg\min_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
+\item \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
+\item based on GP posterior of first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}: decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next
+\item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
+\item objective: minimize \emph{simple regret} 
+$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Entropy Search}
+\begin{itemize}
+\item Let
+   \begin{itemize}
+   \item $p^\star(x \vert \mathcal{D}_n)$ denote the posterior distribution (after observing $\mathcal{D}_n$) of the unknown optimizer $\mathbf{x}^\star = \arg\max_{\mathbf{x} \in \mathcal{X}} f(\mathbf{x})$.
+   \item $H(\mathbf{x}^\star \vert \mathcal{D}_n)$ denote the differential entropy of $p^\star(x \vert \mathcal{D}_n)$
+   \end{itemize}
+   \item Entropy Search (ES)\footcite{hennig_entropy_2012} is an information theoretic acquisition fct.:
+$$a_{ES}(\mathbf{x}, \mathcal{D}_n) = H(\mathbf{x}^\star \vert \mathcal{D}_n) - \mathbb{E}_{y \vert \mathbf{x}, \mathcal{D}_n}   [H(\mathbf{x}^\star \vert \mathcal{D}_n \cup \{(\mathbf{x}, y))]$$
    \end{itemize}
    \pause
-  Parameterized skill \footcite{da_silva_learning_2012}:
-  \begin{itemize}
-    \item Learn a function $\hat{\Theta}: \taskparam \mapsto \skillparam_\taskparam$ from task vector $\taskparam$ to a skill vector $\skillparam_\taskparam$
-    \item Objective: $\hat{\Theta}$ similar to $\Theta^* = \arg\max_\Theta \int P(\taskparam)J(\Theta(\taskparam),\taskparam)d\taskparam$
-    \item Typically: $\hat{\Theta}(\taskparam) \neq \arg\max_\skillparam J(\skillparam,\taskparam)$
-  \end{itemize}
-  \pause
-  Our approach: give more than point estimate $\hat{\Theta}(\taskparam)$
+
+   \vspace*{-.25cm}
+   \begin{figure}
+   \centering
+   \includegraphics[width=0.48\columnwidth]{../pics/regret_illustration_2}
+   \visible<3->{
+     \includegraphics[width=0.48\columnwidth]{../pics/regret_scatter}
+   }
+   \vspace*{-.25cm}
+   \caption{(Left) GP posterior, probability of maximum $p^\star$, and expected regret ER.
+(Right) Scatter plot of  position of optimum and regret of $\mathbf{\tilde x} = 1.5$ versus optimum in sample functions.}
+   \label{fig:MRS_illustration}
+   \end{figure}
 \end{frame}
 
-\begin{frame}{Learning Skill Templates}
-  Given:
+\begin{frame}{Minimum Regret Search}
+
+MRS: acquistion function based directly on external objective of minimizing simple regret
 \begin{itemize}
-    \item Training set from $K$ source tasks $E = \left\{(\taskparam_i, \skillparam_{\taskparam_i}) \vert i=1,\dots,K\right\}$ with $J(\skillparam_{\taskparam_i},\taskparam_i) \approx J(\skillparam_{\taskparam_i}^*,\taskparam_i)$
-    \item $E$ can be generated using RL (e.g., direct policy search) in each of the tasks
-  \end{itemize}
- \pause
- Skill Templates
- \begin{itemize}
-    \item \emph{Goal}: Transfer procedural knowledge contained in $E$ to novel, $(K+1)$st tasks $\tau$
-    \item \emph{Idea}: learn to initialize policy search for new task such that close-to-optimal policies can be learned more sample-efficiently
-    \item Skill template: $\psi: \taskparam \mapsto \mathcal{N}(\Theta(\taskparam), \Omega(\taskparam))$
-    \item Normal distribution over policy parameter space, where
-    \begin{itemize}
-      \item $\Theta(\taskparam) \in \mathbb{R}^m$ determines starting point for policy search
-      \item $\Omega(\taskparam) \in \mathbb{R}^{m\times m}$ controls initial exploration
-    \end{itemize}
-    \item Skill template learned from $E$
+ \item Expected simple regret: $\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
+= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
+x})]$
+ \item For fixed GP $p(f)$, $\arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
+ \item MRS aims at selecting query points s.t. ER is minimized also with respect to resulting $p(f)$
+ \item Myopic choice: select next query point s.t. minimum ER is reduced the most (in expectation)
+  $$a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
+  = \min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x})
+   - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]$$
+ \item MRS additionally also accounts for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ 
+  $$a_{\text{MRS}}(\mathbf{x}^q)
+    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}[\text{ER}(p_n)(\mathbf{\tilde x})] 
+     - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[
+      \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n \cup \{(\mathbf{x}^q, y)\}}}[
+       \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]]$$
 \end{itemize}
@@
 
-\begin{frame}{Approach}
+\begin{frame}{Minimum Regret Search Illustration}
+\begin{figure}
+\centering
+\includegraphics[width=0.48\columnwidth]{../pics/acq_comparison}
+\end{figure}
+
 \begin{itemize}
-    \item Represent skills using dynamical systems movement primitives (DMPs)\footcite{Ijspeert2013}\footcite{mulling_learning_2012}
-    \item Learn source task policies using policy search based on CMA-ES \footcite{hansen_completely_2001}
-    \item Learn $\Theta: \taskparam \mapsto \skillparam_\taskparam$ from E using Gaussian Process Regression (GPR) \footcite{rasmussen_gaussian_2006}
-    \item Restrict $\Omega$ to the diagonal case {\tiny [for now]}:
-    \begin{enumerate}
-      \item Weight-proportional exploration: $\Omega(\taskparam)_{ii}$ proportional to $\vert\Theta(\taskparam)_i\vert$
-      \item Uncertainty exploration: $\Omega(\taskparam)_{ii}$ proportional to uncertainty in GPR's prediction of $\Theta_i$
-    \end{enumerate}
-    \item Normalize mean eigenvalue of $\Omega(\taskparam)$
+\item MRS$^\text{point}$ tends to query in areas which are risky for current recommendation (large simple regret possible)
+\item MRS is more smooth than MRS$^\text{point}$ since it accounts for uncertainty in recommendation
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Experimental Setup}
+Synthetic Single-Task Benchmark:
+\begin{itemize}
+ \item Target functions sampled from a generative model on $\mathcal{X} = [0, 1]^2$ 
+ \item In practice: 
+   \begin{itemize} 
+   \item sample $250$ pairs $(\mathbf{x}, f(\mathbf{x}))$ from function $f \sim GP(f)$
+   \item fit another GP to these pairs
+   \item use resulting posterior mean as target function
+   \end{itemize}
+ \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
+ \item Probabilistic surrogate model used in BO:\\ GP with isotropic RBF kernel of length scale $l = 0.1$ and unit signal variance
+ \pause
+ \item Generative model
+    \begin{itemize} 
+    \item without model mismatch: GP with isotropic RBF kernel ($l = 0.1$ and unit signal variance)
+    \item with model mismatch:  GP with isotropic rational quadratic kernel ($l = 0.1$, $\alpha=1.0$ and unit signal variance)
+    \end{itemize}
 \end{itemize}
@@
 
-\begin{frame}{Test domain}
-  \begin{itemize}
-    \item Learn to throw a ball with a simulated PA-$10$
-    \item $\taskparam \in \mathbb{R}^2$: target position on floor
-    \item $\skillparam \in \mathbb{R}^{96}$: DMP parameters controlling robot in joint space ($8$ joints):
-    \begin{itemize}
-      \item Joint's trajectory ($10$ parameters per joint)
-      \item Joint's final position and velocity ($2$ parameters per joint)
-    \end{itemize}
-    \item $J(\skillparam,\taskparam)$: Negative of squared distance of thrown ball from target
-  \end{itemize}
-  \begin{center}
-    \includegraphics[width=.6\linewidth]{PA10_Throwing_Ball}
-  \end{center}
+\begin{frame}{Results: No model-mismatch}
+\begin{figure}
+\centering
+\includegraphics[width=.7\columnwidth]{../pics/empirical_comparison} \\
+\includegraphics[width=.7\columnwidth]{../pics/hist}
+\end{figure}
 \end{frame}
 
-\begin{frame}{Illustration: Ball Throwing (1/2)}
-   \begin{center}
-   Error of $\Theta(\taskparam)$ vs.\,Number of Source Tasks
-   \end{center}
-   \begin{center}
-         \only<1>{\includegraphics[width=\linewidth]
-                   {plots/prediction_error_00}}
-         \only<2>{\includegraphics[width=\linewidth]
-                   {plots/prediction_error_01}}
-         \only<3>{\includegraphics[width=\linewidth]
-                   {plots/prediction_error_03}}
-         \only<4>{\includegraphics[width=\linewidth]
-                   {plots/prediction_error_05}}
-         \only<5>{\includegraphics[width=\linewidth]
-                   {plots/prediction_error_09}}
-   \end{center}
+\begin{frame}{Results: }
+\begin{figure}
+\centering
+\includegraphics[width=.8\textwidth]{../pics/es_analysis}
+\label{fig:es_analysis}
+\end{figure}
+
+Acquisition functions on a target function at $N=100$ and 25 representer points; darker areas correspond to larger values.
+ES focuses on sampling in areas with high density of $p^\star$ (many representer points), while MRS focuses on unexplored areas that are populated by representer points (non-zero $p^\star$).
+
 \end{frame}
 
-\begin{frame}{Illustration: Ball Throwing (2/2)}
-   \begin{center}
-   Error during Learning (Tabula Rasa vs.\,Skill Template (Uncertainty))
-   \end{center}
-   \begin{center}
-         \only<1>{\includegraphics[width=\linewidth]
-                   {plots/error_during_learning_00}}
-         \only<2>{\includegraphics[width=\linewidth]
-                   {plots/error_during_learning_01}}
-         \only<3>{\includegraphics[width=\linewidth]
-                   {plots/error_during_learning_02}}
-         \only<4>{\includegraphics[width=\linewidth]
-                   {plots/error_during_learning_03}}
-         \only<5>{\includegraphics[width=\linewidth]
-                   {plots/error_during_learning_04}}
-         \only<6>{\includegraphics[width=\linewidth]
-                   {plots/error_during_learning_05}}
-   \end{center}
+\begin{frame}{Results: Model-mismatch}
+\begin{figure}
+\centering
+\includegraphics[width=.7\textwidth]{../pics/empirical_comparison_mm} \\
+\includegraphics[width=.7\textwidth]{../pics/hist_mm}
+\end{figure}
 \end{frame}
 
-\begin{frame}{Results: Ball Throwing}
-   \begin{center}
-   Learning Curve (Tabula Rasa vs.\,ST with different $\Omega$)
-   \end{center}
-   \begin{center}
-         \includegraphics[width=.8\linewidth]{plots/learning_curve}\\
-         Initial exploration covariance matrix matters (even with CMA-ES)
-   \end{center}
-\end{frame}
+\begin{frame}{Outlook}
 
-\begin{frame}{Outlook and Discussion}
-  Open questions and future work:
   \begin{itemize}
-    \item Correlated skill parameter dimensions: how to learn non-diagonal $\Omega \in \mathbb{R}^{m \times m}$ from small set of source tasks?
-    \item Off-task learning: how to learn from $\skillparam_{\taskparam}$ with $J(\skillparam_{\taskparam},\taskparam) \ll J(\skillparam_{\taskparam}^*,\taskparam)$?
-    \item Best way to handle discontinuities in mapping $\Theta$ (like fore- vs.\,backhand)?
-    \item Learn $\Theta$ using (non-parametric) regression or (parametric) policy search?
+    \item Additional content of the paper:
+    \begin{itemize}
+      \item Multi-task Minimum regret search
+      \item results on simulated robotic task
+    \end{itemize}
     \pause
-    \item Evaluation on humanoid robot AILA (simulated and real)
+    \item Future work:
+    \begin{itemize}
+      \item treatment of GP hyperparameters
+      \item more efficient approximation techniques for MRS
+    \end{itemize}
+    \pause
+    \item Source code available at: \url{https://github.com/jmetzen/bayesian_optimization}
   \end{itemize}
 
-  \begin{center}
-    \includegraphics[width=.39\linewidth]{AILA}
-  \end{center}
+  \vspace*{1.5cm}
   \pause
   \begin{center}
-   Thank you for your attention!
+   Thank you for your attention! \\
    Do you have questions, comments, or ideas?

### 2016-06-08 2016_ICML/poster/content/left_column.tex
Revising poster

@@
 \begin{itemize}
-\item black-box optimization problems $\mathbf{x} = \arg\min_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
+\item black-box optimization problems $\mathbf{x} = \arg\max_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
 \item maintains a \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
-\item decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next based on GP posterior of first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}
+\item decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next based on GP posterior after first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}
 \item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
@@
  \item For fixed GP $p(f)$, $\arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
- \item MRS aims at selecting query points s.t. ER is minimized also with respect to resulting $p(f)$
- \item Myopic choice: select next query point s.t. minimum ER is reduced the most (in expectation)
+ \item MRS aims at selecting query points s.t.\  ER is minimized also with respect to resulting $p(f)$
+ \item Myopic choice: select next query point s.t.\ minimum ER is reduced the most (in expectation)
  \item $a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
@@
 	 - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]$
- \item Additionally also account for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ yields MRS
+ \item Additionally also accounting for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ yields MRS
  \item $a_{\text{MRS}}(\mathbf{x}^q)
-    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}[\text{ER}(p_n)(\mathbf{\tilde x})] 
+    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n}}[\text{ER}(p_n)(\mathbf{\tilde x})] 
 	   - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[
@@
  \item estimating $p^\star_{\mathcal{D}_n}$ on representer points by reusing the samples used 
-for approximating $\mathbb{E}_{p(f)}$
+for approximating $\mathbb{E}_{p(f)}$ (incurs a small bias)
 \item Common random numbers in estimation of

### 2016-06-08 2016_ICML/poster/content/right_column.tex
Revising poster

@@
 of length scale $l = 0.1$ and unit signal variance) on $\mathcal{X} = [0, 1]^2$ 
- \item In practice: sample $250$ function values from GP, fit GP to these function values and use resulting posterior mean as target function
+ \item In practice: sample $250$ function values from GP, fit GP to these function values, and use resulting posterior mean as target function
  \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
@@
  \item For multi-task MRS and results on simulated robotic task: see paper
- \item Open questions: treatment of GP hyperparameters, more efficient approximation techniques for MRS, regret bounds for MRS?
+ \item Open questions: treatment of GP hyperparameters, more efficient approximation techniques for MRS, are there regret bounds for MRS?
  \item Source code: \url{https://github.com/jmetzen/bayesian_optimization}

### 2016-06-08 2016_ICML/presentation/main.tex
First version of ICML presentation

@@
 
-\begin{frame}{Motivation: Bayesian optimization}
+\begin{frame}{Introduction}
 
+\begin{itemize}
+  \item Motivation: optimization of expensive target functions
+  \item Examples:
+  \begin{itemize}
+    \item Automated machine learning (computational cost)
+    \item Process optimization (economical cost)
+    \item Robot learning (supervision cost)
+    \item Animal testing (moral cost)
+  \end{itemize}
+  \pause
+  \item Objective: Find approximate optimum of target function with a very small number of function evaluations (``queries'')
+  \pause
+   \item Approach: Invest significant amounts of computation to determine ``optimal'' sequence of query points
+\end{itemize}
+\vspace*{4cm}
 \end{frame}
@@
 \begin{frame}{Bayesian Optimization}
-\textbf{Bayesian optimization}\footcite{shahriari_taking_2016}:
+Bayesian optimization\footcite{shahriari_taking_2016}:
 \begin{itemize}
-\item black-box optimization problems: $\mathbf{x} = \arg\min_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
+\item black-box optimization problems: $\mathbf{x} = \arg\max_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
 \item \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
@@
 \end{itemize}
+\vspace*{2cm}
 \end{frame}
@@
 \begin{itemize}
-\item Let
-   \begin{itemize}
-   \item $p^\star(x \vert \mathcal{D}_n)$ denote the posterior distribution (after observing $\mathcal{D}_n$) of the unknown optimizer $\mathbf{x}^\star = \arg\max_{\mathbf{x} \in \mathcal{X}} f(\mathbf{x})$.
-   \item $H(\mathbf{x}^\star \vert \mathcal{D}_n)$ denote the differential entropy of $p^\star(x \vert \mathcal{D}_n)$
-   \end{itemize}
+    \item Let $p^\star(x \vert \mathcal{D}_n)$ denote the posterior distribution (after observing $\mathcal{D}_n$) of the unknown optimizer $\mathbf{x}^\star = \arg\max_{\mathbf{x} \in \mathcal{X}} f(\mathbf{x})$.
+    \item and $H(\mathbf{x}^\star \vert \mathcal{D}_n)$ denote the differential entropy of $p^\star(x \vert \mathcal{D}_n)$
     \item Entropy Search (ES)\footcite{hennig_entropy_2012} is an information theoretic acquisition fct.:
@@
    \centering
-   \includegraphics[width=0.48\columnwidth]{../pics/regret_illustration_2}
+   \includegraphics[width=0.48\columnwidth]{../pics/regret_illustration_3}
    \visible<3->{
@@
    \vspace*{-.25cm}
-   \caption{(Left) GP posterior, probability of maximum $p^\star$, and expected regret ER.
-(Right) Scatter plot of  position of optimum and regret of $\mathbf{\tilde x} = 1.5$ versus optimum in sample functions.}
+   \caption{\tiny (Left) GP posterior, probability of maximum $p^\star$, and expected regret ER.
+\visible<3->{(Right) Scatter plot of  position of optimum and regret of $\mathbf{\tilde x} = 1.5$ versus optimum in sample functions.}}
    \label{fig:MRS_illustration}
@@
 
-\begin{frame}{Minimum Regret Search}
+\begin{frame}{Minimum Regret Search (MRS)}
 
-MRS: acquistion function based directly on external objective of minimizing simple regret
+Acquisition function based directly on minimizing simple regret
 \begin{itemize}
@@
  \item For fixed GP $p(f)$, $\arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
- \item MRS aims at selecting query points s.t. ER is minimized also with respect to resulting $p(f)$
- \item Myopic choice: select next query point s.t. minimum ER is reduced the most (in expectation)
+\only<2->{
+ \item MRS aims at selecting query points s.t.\ ER is minimized also with respect to resulting $p(f)$
+ \item Myopic choice: MRS$^{\text{point}}$ selects next query point s.t.\ minimum ER is reduced the most (in expectation)
   $$a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
@@
    - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]$$
+ \visible<3->{
  \item MRS additionally also accounts for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ 
   $$a_{\text{MRS}}(\mathbf{x}^q)
-    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}[\text{ER}(p_n)(\mathbf{\tilde x})] 
+    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n}}[\text{ER}(p_n)(\mathbf{\tilde x})] 
      - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[
@@
        \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]]$$
+  }
+  }
 \end{itemize}
-
+\only<1>{
+\begin{center}
+\includegraphics[width=0.58\columnwidth]{../pics/regret_illustration_4}
+\end{center}
+}
 \end{frame}
 
-\begin{frame}{Minimum Regret Search Illustration}
+\begin{frame}{Illustration of Acquisition Functions}
 \begin{figure}
 \centering
-\includegraphics[width=0.48\columnwidth]{../pics/acq_comparison}
+\includegraphics[width=0.48\columnwidth]{../pics/acq_comparison_2}
 \end{figure}
 
+\vspace*{-.5cm}
 \begin{itemize}
+\item ES tends to query close to areas where $p^\star$ is large
 \item MRS$^\text{point}$ tends to query in areas which are risky for current recommendation (large simple regret possible)
@@
 
-\begin{frame}{Results: }
-\begin{figure}
-\centering
-\includegraphics[width=.8\textwidth]{../pics/es_analysis}
-\label{fig:es_analysis}
-\end{figure}
-
-Acquisition functions on a target function at $N=100$ and 25 representer points; darker areas correspond to larger values.
-ES focuses on sampling in areas with high density of $p^\star$ (many representer points), while MRS focuses on unexplored areas that are populated by representer points (non-zero $p^\star$).
-
-\end{frame}
-
 \begin{frame}{Results: Model-mismatch}
@@
   \begin{center}
-   Thank you for your attention! \\
+   Thank you for your attention and see you at the poster! \\
    Do you have questions, comments, or ideas?
@@
 
+\begin{frame}{Results: MRS versus ES}
+\begin{figure}
+\centering
+\includegraphics[width=.8\textwidth]{../pics/es_analysis}
+\label{fig:es_analysis}
+\end{figure}
+
+Acquisition functions on a target function at $N=100$ and 25 representer points; darker areas correspond to larger values.
+ES focuses on sampling in areas with high density of $p^\star$ (many representer points), while MRS focuses on unexplored areas that are populated by representer points (non-zero $p^\star$).
+
+\end{frame}
+
 \end{document}

### 2016-06-09 2016_ICML/presentation/main.tex
Revising presentation

@@
 \begin{frame}{Bayesian Optimization}
-Bayesian optimization\footcite{shahriari_taking_2016}:
+Bayesian optimization\footcite{shahriari_taking_2016} in a nutshell:
 \begin{itemize}
@@
 \item \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
-\item based on GP posterior of first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}: decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next
-\item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
+\pause
+\item For $n=1\dots N$:
+\begin{itemize}
+   \item determine GP posterior $p(f\vert \mathcal{D}_n)$ for $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ 
+   \item decide on a query point based on \emph{acquisition function} $a$: $\mathbf{x}_{n+1} = \arg\max_{\mathbf{x} \in \mathcal{X}} a_{p(f\vert \mathcal{D}_n)}(x) $
+\item observe (potentially noisy) $y_{n+1} = f(\mathbf{x}_{n+1}) + \epsilon$
+\end{itemize}
+\pause
+\item recommend $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
 \item objective: minimize \emph{simple regret} 
@@
 \begin{frame}{Experimental Setup}
-Synthetic Single-Task Benchmark:
+Synthetic Single-Task Benchmark\footcite{hennig_entropy_2012}:
 \begin{itemize}
@@
    \begin{itemize} 
-   \item sample $250$ pairs $(\mathbf{x}, f(\mathbf{x}))$ from function $f \sim GP(f)$
-   \item fit another GP to these pairs
+   \item sample $250$ pairs $(\mathbf{x}, f(\mathbf{x}))$ from function $f \sim p(f)$
+   \item fit GP to these pairs
    \item use resulting posterior mean as target function
@@
  \pause
- \item Generative model
+ \item Generative model $p(f)$
     \begin{itemize} 
@@
     \begin{itemize}
-      \item Multi-task Minimum regret search
+      \item multi-task minimum regret search
       \item results on simulated robotic task

### 2016-06-13 2016_ICML/poster/content/left_column.tex
Minor changes in poster

@@
 \justifying
-We propose minimum regret search (MRS), a novel acquisition function for Bayesian
+We propose minimum regret search (MRS), a \emph{novel acquisition function} for Bayesian
 optimization. MRS bears similarities with information-theoretic approaches
 such as entropy search (ES). However, while ES aims in each query at maximizing the
-information gain with respect to the global maximum, MRS aims at minimizing the
-expected simple regret of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
+information gain with respect to the global maximum, MRS aims at \emph{minimizing the
+expected simple regret} of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
 cases, MRS produces fewer outliers with high simple regret than ES. We provide empirical
@@
 \item decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next based on GP posterior after first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}
-\item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
+\item recommends $\mathbf{\tilde x}_N$ as optimum after $N$ queries (optimum of GP or best query point)
 \item objective: minimize \emph{simple regret} 
@@
 
-\begin{block}{\blocktitle{Minimum Regret Search}}
+\begin{block}{\blocktitle{Minimum Regret Search (MRS)}}
 
-Minimum regret search (MRS): acquistion function based directly on external objective of minimizing simple regret
+Acquistion function based directly on external objective of minimizing simple regret
 \begin{itemize}

### 2016-06-14 2016_ICML/poster/content/left_column.tex
Changes for final version of poster
Working on presentation

@@
   = H(\mathbf{x}^\star \vert \mathcal{D}_n) - \mathbb{E}_{y \vert \mathbf{x}, \mathcal{D}_n}
-	[H(\mathbf{x}^\star \vert \mathcal{D}_n \cup \{(\mathbf{x}, y))]$,
+	[H(\mathbf{x}^\star \vert \mathcal{D}_n \cup \{(\mathbf{x}, y)\})]$,
 	where $H(\mathbf{x}^\star \vert \mathcal{D}_n)$ denotes the differential entropy
@@
 
-Acquistion function based directly on external objective of minimizing simple regret
+Acquisition function based directly on external objective of minimizing simple regret
 \begin{itemize}

### 2016-06-14 2016_ICML/presentation/main.tex
Working on presentation

@@
 
-\usepackage{animate}
+\usepackage{xcolor}
+\usepackage{mathtools}
+
+\makeatletter
+\newcommand{\redub}{}
+\def\redub#1{%
+  \@ifnextchar_%
+    {\@redub{#1}}
+    {\@latex@warning{Missing argument for \string\redub}\@redub{#1}_{}}%
+}
+\def\@redub#1_#2{%
+    \colorlet{currentcolor}{.}%
+    \color{red}%
+    \underbrace{\color{currentcolor}#1}_{\color{red}#2}%
+    \color{currentcolor}%
+}
+\makeatother
 
@@
 \renewcommand{\emph}[1]{\textbf{#1}}
-
-\newcommand{\taskparam}{{\color{red} \tau}}
-\newcommand{\skillparam}{{\color{blue} \theta}}
-
-%\newcommand{\newblock}{}
 
@@
   \pause
-  \item Objective: Find approximate optimum of target function with a very small number of function evaluations (``queries'')
+  \item Objective: Find close-to-optimal value of target function with a very small number of function evaluations (``queries'')
   \pause
@@
 \pause
-\item recommend $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
+\item recommend $\mathbf{\tilde x}_N$ as optimum  after $N$ queries (optimum of GP or best query point)
 \item objective: minimize \emph{simple regret} 
@@
     \item Entropy Search (ES)\footcite{hennig_entropy_2012} is an information theoretic acquisition fct.:
-$$a_{ES}(\mathbf{x}, \mathcal{D}_n) = H(\mathbf{x}^\star \vert \mathcal{D}_n) - \mathbb{E}_{y \vert \mathbf{x}, \mathcal{D}_n}   [H(\mathbf{x}^\star \vert \mathcal{D}_n \cup \{(\mathbf{x}, y))]$$
+$$a_{ES}(\mathbf{x}, \mathcal{D}_n) = \redub{H(\mathbf{x}^\star \vert \mathcal{D}_n)}_{\text{current entropy}} 
+- \redub{\mathbb{E}_{y \vert \mathbf{x}, \mathcal{D}_n}   [H(\mathbf{x}^\star \vert \mathcal{D}_n \cup \{(\mathbf{x}, y)\})]}_{\text{expected posterior entropy for query at } \mathbf{x}}$$
    \end{itemize}
@@
    \vspace*{-.25cm}
-   \caption{\tiny (Left) GP posterior, probability of maximum $p^\star$, and expected regret ER.
+   %\caption{\tiny (Left) GP posterior, probability of maximum $p^\star$, and expected regret ER.
 \visible<3->{(Right) Scatter plot of  position of optimum and regret of $\mathbf{\tilde x} = 1.5$ versus optimum in sample functions.}}
@@
 
-Acquisition function based directly on minimizing simple regret
+Acquisition function based on minimizing the expected simple regret
 \begin{itemize}
@@
 x})]$
- \item For fixed GP $p(f)$, $\arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
+ \only<1>{
+ \item For fixed GP $p(f)$, $\mathbf{\tilde x} = \arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
+ }
  \only<2->{
@@
   $$a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
-  = \min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x})
-   - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]$$
+  = \redub{\min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x})}_{\text{current minimum ER}}
+   - \redub{\mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]}_{\text{expected posterior minimum ER for query at } \mathbf{x}^q}$$
  \visible<3->{
- \item MRS additionally also accounts for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ 
+ \item Minimizer $\arg\min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x})$ can be seen as point estimate for $\mathbf{\tilde x}_N$ 
+ \item MRS additionally also accounts for uncertainty regarding $\mathbf{\tilde x}_N$: 
   $$a_{\text{MRS}}(\mathbf{x}^q)
@@
    \end{itemize}
+ \pause
  \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
@@
 
-\begin{frame}{Outlook}
+\begin{frame}{Summary and Outlook}
 
   \begin{itemize}
+    \item Contribution: Novel acquisition which explicitly aims at minimizing the expected simple regret
+    \pause
     \item Additional content of the paper:
@@
 
-  \vspace*{1.5cm}
+  \vspace*{1cm}
   \pause
@@
 
-\begin{frame}{Results: MRS versus ES}
+\appendix
+
+\begin{frame}[noframenumbering]{Results: MRS versus ES}
 \begin{figure}

### 2016-06-14 2016_ICML/poster/defines/header.tex
Changes for final version of poster
Moving title down

--- 2016-05-27 2016_ICML/poster/defines/header.tex
@@
-\pgfdeclareimage[height=4.8cm]{dfki-logo}{./defines/DFKI_Schrift}
+\pgfdeclareimage[height=2.8cm]{dfki-logo}{./defines/Bosch-Logo.pdf}
 
@@
    \begin{beamercolorbox}{mycolor}
-    \centering{\parbox{70cm}{\centering{\huge{\textbf{\inserttitle}}}}}\\[5mm]
-    \centering{\parbox{70cm}{\centering{\Large{\insertauthor\\[.5cm] University Bremen,
-Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen,
-Germany\hspace{2cm}}}}}
+    \raisebox{-1.5cm}{\centering{\parbox{70cm}{\centering{\huge{\textbf{\inserttitle}}}}}}
+
+    \centering{\parbox{70cm}{\centering{\Large{\raisebox{-1.5cm}{\insertauthor}\\[.5cm] 
+    University Bremen, Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen, Germany\\
+    Robert Bosch GmbH, Corporate Research CR/AEY2, 70442 Stuttgart, Germany}
+}}}
 

### 2016-06-15 2016_ICML/presentation/main.tex
Two minor bug fixes in presentation

@@
   \pause
-   \item Approach: Invest significant amounts of computation to determine ``optimal'' sequence of query points
+   \item Approach: Invest significant amounts of computation time to determine ``optimal'' sequence of query points
 \end{itemize}
@@
   \begin{itemize}
-    \item Contribution: Novel acquisition which explicitly aims at minimizing the expected simple regret
+    \item Contribution: Novel acquisition function which explicitly aims at minimizing the expected simple regret
     \pause
